---
title: "script"
author: "APB"
date: "12/16/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#### R Version 1.4.1103 © 2009-2021 RStudio, PBC ; As of 8 April 2021 No new updates ####


rm(list = ls())
library(tidyverse)
library(grid)
####Color Theme####

```


```{r PlotTheme}
  singlefigtheme <- theme_classic() + theme(axis.title.x = element_text(size = 12, face = "bold"),
                       axis.title.y = element_text(size = 12),
                       axis.text.x = element_text(size = 12),
                       axis.text.y = element_text(size = 12))

  multifigtheme <- singlefigtheme + theme(axis.title.x = element_blank(),
                                      axis.text.x = element_blank(),
                                      legend.key = element_rect(colour = NA, fill = NA))

  col3 <- c("#563caa","#563caa","#90aa3c", "#3caa56")
  


```



```{r load_data, include=FALSE}

##Feeding Rate data
data <- read_csv("data/AJV2_6Nov2019_JLH.csv")
names(data)

#Life table data
life <- read_csv("data/LifeTable_AJV2_3Dec2019.csv")
names(life)

#check data
head(data)
head(life)




#merge data together
all.data.joined <- data %>% 
  left_join(life, by = c("Genotype", "Spore_level", "Animal", "Infected_Uninfected", "Sex")) %>%
  mutate(Individual_ID = paste(Genotype, 
                               Spore_level, 
                               Animal, 
                               sep = "_")) 

names(all.data.joined)

#to delete columns you can use the select() command from tidyverse. 
# You can either use select and type the columns you want to keep, or you can use # a minus before the column name to delete it and leave the others.
#removing unnecessary columns. also, you can use select in pipelines

all.data.joined <- all.data.joined %>% 
  dplyr::select(-c( "Length_Day_7", "Length_Day_20", "DOB", "Total_Offspring"))


#instead of using subset, better use filter from tidyverse
##Remove males from dataframe

#all.female <- subset(all.data.joined, all.data.joined$Sex == "F")

all.female <- all.data.joined %>% 
  filter(Sex == "F")

```


```{r load_PO_data, echo = FALSE}

#### LOAD PO DATA ####
##adding AJ2 active phenoloxidase data
## JLH My changes here are b/c it looked like these calculations weren't averaged over the technical replicates? Were they and I missed something? The code below should calculate the mean for each biological replicate, which can then be used to calculate delta PO or whatever.
## I have not looked yet to see whether or not this changed any of the results. 
all_po_data <- read_csv("data/AJ2_PO_for_R.csv")
names(all_po_data)
head(all_po_data)

#all this cleaning can be done in a dplyr pipeline. Much nicer to see and to #read!
##cleaning PO data 

##Removing time point 0

#here you called this dataframe po_data, but I assumed you wanted to mantain #the name all_po_data, right? the po_data wasn't used anywhere else in this #report, so I assumed it was just a typo
all_po_data <- all_po_data %>% 
  filter(Time != 0) %>% 
  filter(!is.na(Abs)) %>%  #filter out NAs
  mutate(Abs = as.numeric(Abs), 
         Prop_inf = as.numeric(Prop_inf))


names(all_po_data)
head(all_po_data)

length(all_po_data)
all_po_data
#### po_data includes:Genotypes (control=PBS), Spores (exposed to), ####
## Sample (sample number), Replicate (2 reps from each sample),
## time (in hours), Abs (absorbance value), and 
## Prop_inf (proportion of infected individuals in the sample)

# GOALS:
# (1) take the average for each technical replicate
# (2) calculate delta PO: take the mean_po at time point 4.5 and subtract it from mean_po at time point 1.0
# (3) add that data frame to the dataframe above (all.data)
clone.names <- as.character(unique(all_po_data$Genotype))
clone.names

# Here, the mean we want to calculate doesn't work because the na in the original dataframe
# are not real R's NA, but they are just character strings na. Two possible solutions:
# you delete the rows where those na are, or you change those na into proper NA. 
# I chose the second solution, at line 154/155 (transformed into numeric first, because it was a factor)


avg_po1 <- all_po_data %>% 
  filter(Genotype != "Control") %>% 
  mutate(Abs = ifelse(Abs == "na", NA, Abs)) %>% 
  mutate(Abs = as.numeric(Abs)) %>% 
  arrange(Genotype, Spores, Time, Replicate, Sample) %>% 
  group_by(Genotype, Spores) %>%
  mutate(mean_po = mean(Abs, na.rm = T)) %>% 
  select(Genotype, Spores, mean_po) %>% 
  distinct() %>% as.data.frame()
avg_po1 



#### CALCULATE DELTA PO ####

# # subset the data to only include time "4.5"
final <- subset(all_po_data, all_po_data$Time == "4.5")
final$Abs
# # 
# # ### Now look at the change in abs which equivalent to the amount of active PO produced ####
# # #ADD CHANGE IN ABS (ACTIVE PHENOLOXIDASE)
initial <- subset(all_po_data, all_po_data$Time == 1)
initial$Abs
# # 
# 
# # if you run this, remember to convert factors to numeric (both final$abs and
# # intiial$abs are factors, you have to convert them to numeric), like
final$Abs <- as.numeric(final$Abs)
initial$Abs <- as.numeric(initial$Abs)

# #calculating the change in absorbance
delta_po <- final$Abs - initial$Abs
# 
# # multiplying by 1000 to get "activity units" (Mucklow & Ebert, 2003)
delta_po <- delta_po*1000
# # adding the delta_po values back to dataframe
initial$delta_po <- delta_po
# 


#### LOAD PO DATA ####
##adding AJ2 active phenoloxidase data
## updated 3/10/21
all_po_data <- read_csv("data/AJ2_PO_for_R.csv")
names(all_po_data)
head(all_po_data)


#### Now look at the change in abs which equivalent to the amount of active PO produced ####
#find initial absorbances
initial <- subset(all_po_data, all_po_data$Time == 1)

#find final absorbances
po4.5 <- subset(all_po_data, all_po_data$Time == "4.5")
#calculate the change in absorbance

delta_po <- po4.5$Abs - initial$Abs
# multiplying by 1000 to get "activity units" (Mucklow & Ebert, 2003)
delta_po <- delta_po*1000
# adding the delta_po values back to dataframe
initial$delta_po <- delta_po
#average across replicates and divide by the number of individuals in the sample
po <- initial %>%
  group_by(Genotype, Spores, Sample, Prop_inf, No_in_sample) %>%
  summarise(delta_po = mean(delta_po))

po$cor_delta_po <- po$delta_po/po$No_in_sample

po <- subset(po, Genotype != "Control")

names(po)[2]<-"Spore_level"







```


```{r calculate_feeding_rate_means_for_each_individual, include = TRUE}

#### Means of the controls  - these means for each treatment (i.e., plate_control) are then used in the calculation below ####
 
#in this case, it is better to use a summarise instead than a mutate and distinct. You will get the same result, but code is much cleaner




summary_df <- all.female %>% 
   group_by(Plate_Control) %>%
   summarise(Control_mean = mean(USE_Control_Flour_Reading, na.rm = T))



#match control mean with plate treatment
all.female <- all.female %>%
  left_join(summary_df, by = c("Plate" = "Plate_Control"))


v <- 10 
## volume, mL
t <- 7  
##time, hours

k <- all.female$Control_mean/all.female$Flourometry_Reading
k
##difference in feeding compared to control

##calculate feeding rate (Sarnelle and Wilson)
all.female$fr_sw <- log(k) * (v/t)


#calculate mean fluor reading per animal (keep rate > 0)
animal_mean <- all.female %>%
  filter(fr_sw > 0.009) %>%
  filter(fr_sw < 0.4 ) %>%
  #group based on these variables
  group_by(Genotype, Spore_level, Animal, Plate, Control_mean) %>%
  #means based on groups above
  summarise(mean_surface_area = mean(Size_mm2, na.rm = TRUE),
            mean_init_length = mean(Length_mm, na.rm = TRUE),
            mean_final_length = mean(Final_length_mm, na.rm = TRUE),
            mean_final_surface_area = mean(Final_Size_mm2, na.rm = TRUE),
            mean_growth_length = mean(Total_Growth, na.rm = TRUE),
            mean_feeding_rate = mean(fr_sw, na.rm = TRUE),
            ss_fr = mean_feeding_rate/mean_surface_area,
            susc = mean(Susceptible, na.rm = TRUE),
            inf = mean(Infected, na.rm = TRUE),
            censured = mean(Censured, na.rm = TRUE),
            spores_ul = mean(Spores_ul, na.rm = TRUE),
            fecundity = mean(Total_Fecundity, na.rm = TRUE),
            survival = mean(TimeTillDeathDays, na.rm = TRUE),
            age_clutch_1 = mean(Age_1st_clutch, na.rm = TRUE))
animal_mean

```






```{r remove exposed but uninfected animals, include = TRUE}
## I'm removing these animals b/c I think it complicates the story and we can't provide an explanation right now and we also can't say definitively that they weren't infected in the first place and either cleared the infection completely or kept it too low for us to detect. 
## I can just see this be a sticking point for reviewers that it'd be better avoid in the first place. I'm flexible on this - you can try to convince me otherwise by writing out what the text will say about these animals and how we will pre-empt reviewer's concerns on this matter :)




infected <- animal_mean %>%
filter(Spore_level > 0 & inf > 0)
infected
names(infected)
head(infected)


unexposed <- animal_mean %>%
filter(Spore_level == 0)
unexposed
names(unexposed)
head(unexposed)

#merge data together
filtered_df <-  bind_rows(infected, unexposed)
filtered_df

```


```{r}

# Proportion infected
# Need the mean and SE here...mean # infected/genotype and spore level +/- the standard error
# animal_mean_inf <- animal_mean %>% filter(Spore_level > 0) 



  genolabel <- c("Genotype 1", "Genotype 2", "Genotype 3", "Genotype 4") 
  names(genolabel) <- c("A45", "Midland 252", "Midland 281", "Standard")


Pinf <- ggplot(animal_mean, aes(x = Spore_level,  y = 100*inf/(inf + susc) , color = as.factor(Spore_level)))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
  stat_summary(fun.data = mean_se, size = 1,
               alpha = 1.75, position = position_dodge(0.2))+
    #geom_point(position = position_dodge(0.2), size = 4, alpha = 0.30)+
    geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(.~Genotype, nrow = 1, labeller = labeller(Genotype = genolabel))+
    ylab("% Infected") + xlab("")+
    theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 0.25),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #legend.position = c(0.5, 0.9), legend.direction = "horizontal", 
        legend.position = "none",
        strip.text.x = element_text(size = 12, face = "bold"))
Pinf



# Longevity/survival  
  Psurv <- ggplot(animal_mean, aes(x = Spore_level, y = survival, color = as.factor(Spore_level)))+
    geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    #geom_point(position = position_dodge(0.2), size = 4, alpha = 0.30)+
    geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Survival (days post infection)") + xlab(" ")+
    theme(panel.spacing = unit(1.05, "lines"),
      panel.border = element_rect(color = "black", fill = NA, size = 0.25),
      legend.position = "none", strip.text.x = element_blank()) 
    # Add striped background
  Psurv
  

  
library(cowplot)        
  # Put the plots together
  RTPlot1 <- plot_grid(Pinf, Psurv, nrow = 2, align = "v")
  RTPlot1
  ggsave("RTPlot1.png", RTPlot1, height = 10, width = 12, dpi = 600)



``` 




```{r outlier detection for feeding rate data}

animal_mean %>%
  group_by(Genotype, Spore_level) %>%
  ggplot()+
  geom_boxplot(aes(x = Spore_level, y = mean_feeding_rate, color = as.factor(Spore_level)))+
  geom_point(aes(x = Spore_level, y = mean_feeding_rate, color = as.factor(Spore_level)))+
  labs (x = "", y = "") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)

```


```{r tests for normality for feeding rate data}


# Step 1: Test for normality
animal_mean %>%
  group_by(Genotype, Spore_level) %>%
  ggplot()+
  geom_histogram(aes(x = mean_feeding_rate)) +
  labs (x = "", y = "") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype + as.factor(Spore_level))


# Shapiro-Wilk normality test: null = data follow normal distribution. 
# p-value > 0.05 = do not reject null = data follow normal distribution
# p-value < 0.05 = reject teh null = data do not follow normal distribution.

library(outliers)

all.female$fr_sw
geno1 <- with(all.female, subset(all.female, Genotype == "A45"))
n1 <- with(geno1, shapiro.test(geno1$fr_sw))
n1 <- with(geno1, shapiro.test(geno1$fr_sw))
n1 # normal
boxplot.stats(geno1$fr_sw)
test <- grubbs.test(geno1$fr_sw)
test # remove highest value > 0.46


geno2 <- with(all.female, subset(all.female, Genotype == "Midland 252"))
n2 <- with(geno2, shapiro.test(geno2$fr_sw))
n2 # not normal
boxplot.stats(geno2$fr_sw)
test <- grubbs.test(geno2$fr_sw)
test # remove highest value > 0.769


geno3 <- with(all.female, subset(all.female, Genotype == "Midland 281"))
n3 <- with(geno3, shapiro.test(geno3$fr_sw))
n3 <- with(geno3, shapiro.test(geno3$fr_sw))
n3 # normal
boxplot.stats(geno3$fr_sw)
test <- grubbs.test(geno3$fr_sw)
test # 


geno4 <- with(all.female, subset(all.female, Genotype == "Standard"))
n4 <- with(geno4, shapiro.test(geno4$fr_sw))
n4 # normal
boxplot.stats(geno4$fr_sw)
test <- grubbs.test(geno4$fr_sw)
test # remove highest value > 0.4049


 

```

```{r}

 genolabel <- c("Genotype 1", "Genotype 2", "Genotype 3", "Genotype 4") 
  names(genolabel) <- c("A45", "Midland 252", "Midland 281", "Standard")

# Feeding rate - size specific (see Appendix for analyses illustrating links between body size and feeding rates)
Pfeed <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level), y = ss_fr))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
  stat_summary(fun.data = mean_se, size = 1, alpha = 1.75, position = position_dodge(0.2))+
  geom_point(position = position_dodge(0.2), size = 3, alpha = 0.30)+
  #geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+ 
  scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    ylab("Size-specific feeding rate (units)") + xlab("")+
    facet_wrap(.~Genotype, nrow = 1, labeller = labeller(Genotype = genolabel))+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          legend.position = "none",
          #legend.position = c(0.95,0.75),
          legend.title = element_text(size = 10),
          legend.text = element_text(size = 8),
          strip.text.x = element_text(size = 12, face = "bold"))
Pfeed


avg_po1 


# Phenoloxidase
Pphenol <- ggplot(po, aes(x = Spore_level, color = as.factor(Spore_level), y = delta_po))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf, ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
  stat_summary(fun.data = mean_se, size = 1, alpha = 1.75, position = position_dodge(0.2))+
  geom_point(position = position_dodge(0.2), size = 3, alpha = 0.30)+
  #geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+ 
  scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    ylab("Active/Delta phenoloxidase (units)") + xlab("")+
    facet_wrap(.~Genotype, nrow = 1, labeller = labeller(Genotype = genolabel))+
   theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
Pphenol

  

  # Growth
Pgrow <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y = mean_growth_length))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.30)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Growth (change in size + add units)") + xlab("")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
Pgrow
    
    
    # We might want to calculate r here...so that we account for longevity and day of first reproduction
    # Fecundity - size-specific (see Appendix for analyses illustrating links between body size and fecundity) 
Pbirth <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y = (fecundity/mean_final_surface_area)))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.40)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Fecundity (units)") + xlab("")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
Pbirth
   


    # Spore Yield - Size specific (see Appendix for the analyses on the relationship between body size and spore yield)
Pspores <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y =    spores_ul/mean_final_surface_area))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.45)+
    geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+ 
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Size-corrected spore yield (units)") + xlab("Pathogen density (units)")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
 Pspores

library(cowplot)        
  # Put the plots together
  RTPlot2 <- plot_grid( Pfeed, Pphenol, Pgrow, Pbirth, Pspores, nrow = 5, align = "v")
  RTPlot2
  ggsave("RTPlot2.png", RTPlot2, height = 10, width = 12, dpi = 600)

```




```{r}



 genolabel <- c("Genotype 1", "Genotype 2", "Genotype 3", "Genotype 4") 
  names(genolabel) <- c("A45", "Midland 252", "Midland 281", "Standard")




# Feeding rate - size specific (see Appendix for analyses illustrating links between body size and feeding rates)
Pfeed <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level), y = ss_fr))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
  stat_summary(fun.data = mean_se, size = 1, alpha = 1.75, position = position_dodge(0.2))+
  geom_point(position = position_dodge(0.2), size = 3, alpha = 0.30)+
  #geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+ 
  scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    ylab("Size-specific feeding rate (unites)") + xlab("")+
    facet_wrap(.~Genotype, nrow = 1, labeller = labeller(Genotype = genolabel))+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          legend.position = "none",
          #legend.position = c(0.95,0.75),
          legend.title = element_text(size = 10),
          legend.text = element_text(size = 8),
          strip.text.x = element_text(size = 12, face = "bold"))
Pfeed
  

  # Growth
Pgrow <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y = mean_growth_length))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.30)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Growth (change in size + add units)") + xlab("")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
Pgrow
    
    
    # We might want to calculate r here...so that we account for longevity and day of first reproduction
    # Fecundity - size-specific (see Appendix for analyses illustrating links between body size and fecundity) 
Pbirth <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y = (fecundity/mean_final_surface_area)))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.40)+
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Fecundity (units)") + xlab("")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
Pbirth
   


    # Spore Yield - Size specific (see Appendix for the analyses on the relationship between body size and spore yield)
Pspores <- ggplot(filtered_df, aes(x = Spore_level, color = as.factor(Spore_level),  y =    spores_ul/mean_final_surface_area))+
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "grey", color = "NA", alpha = 0.01)+
    stat_summary(fun.data  = mean_se, size = 1, alpha = 1.75,
                 position = position_dodge(0.2))+
    geom_point(position = position_dodge(0.2), size = 3, alpha = 0.45)+
    geom_jitter(width = 0.5, height = 1.85, alpha = 0.30, size = 3)+ 
    scale_color_manual(values = c("#563caa", "darkcyan", "#90aa3c", "#3caa56" , "continuous"), name = "Spore level") +
    singlefigtheme+
    facet_wrap(~Genotype, nrow = 1)+
    ylab("Size-corrected spore yield (units)") + xlab("Pathogen density (units)")+
    theme(panel.spacing = unit(1.05, "lines"),
          panel.border = element_rect(color = "black", fill = NA, size = 0.25),  axis.title.x = element_blank(),
          legend.position = "none", strip.text.x = element_blank())
 Pspores

library(cowplot)        
  # Put the plots together
  RTPlot2 <- plot_grid( Pfeed,Pgrow, Pbirth, Pspores, nrow = 4, align = "v")
  RTPlot2
  ggsave("RTPlot2.png", RTPlot2, height = 10, width = 12, dpi = 600)



```





```{r cost of fitness - ignoring body size and longevity}

#### Calculate the percentage decrease/increase in FECUNDITY across INDIVIDUALS in each genotype, spore treatment ####
# b0 is a per-genotype average
# take each individual in spore treatments 150 and 300 and subtract their birth rate from b0. 

```


```{r net reproductive rate}
# This section needs to calculate the net reproductive rate for a Genotype/spore combination is obtained by multiplying the proportion of females surviving to each age (lx) by the average number of offspring produced at each age (mx) and then adding the products from all the age groups: R0 = Σlxmx. 

# In other words:

# 1)  calculate the number of animals alive at each age (this can be gleaned from 'survival') 
# 2)  calculate the % of surviving in each age class (i.e., # alive on day 7/# alive on day 1) "lx"
# 3)  calculate the mean number of eggs produced each day (fecundity on day x) "mx"
# 4)  add the products from all age groups: R0 = Σlxmx. (again, per genotype and spore level)



```


```{r  spore yield and final size (surface area), echo = FALSE}
# code? In addition, this is down to personal preferences, but I think it is always best separate the dplyr pipeline from the ggplot pipeline, it gives a much cleaner look and it makes easier to spot errors. I commented the grouping line (274) as it is pointless. for ggplot, it doesn't make a difference if a dataframe is grouped or not. I did the same in all the other plotting chunks up to line 433

filtered_df 
  ggplot(filtered_df)+
  geom_point(aes(y = spores_ul,  x = mean_final_surface_area))+
  geom_point(aes(y =  spores_ul, x = mean_final_surface_area, color = as.factor(Spore_level)))+
  labs (y = "spores_ul", x = "mean_final_surface_area") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)


#ggplot(animal_mean, aes(spores_ul, mean_final_surface_area)) + geom_point() + geom_smooth(method = "lm")

```

```{r  spore yield and final size (length), echo = FALSE}


filtered_df 
ggplot(filtered_df)+
  geom_point(aes(y = spores_ul,  x = mean_final_length))+
  geom_point(aes(y =  spores_ul, x = mean_final_length, color = as.factor(Spore_level)))+
  labs (y = "spores_ul", x = "mean_final_length") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)



```

```{r  fecundity and final size (length), echo = FALSE}

filtered_df 
ggplot(filtered_df)+
  geom_point(aes(y = fecundity,  x = mean_final_surface_area))+
  geom_point(aes(y =  fecundity, x = mean_final_surface_area, color = as.factor(Spore_level)))+
  labs (y = "fecundity", x = "mean_final_surface_area") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)


#ggplot(animal_mean, aes(spores_ul, mean_final_surface_area)) + geom_point() + geom_smooth(method = "lm")

```



```{r  feeding rate and initial size (sa), echo = FALSE}
filtered_df %>%
ggplot(filtered_df)+
  geom_point(aes(y = mean_feeding_rate,  x = mean_surface_area))+
  geom_point(aes(y =  mean_feeding_rate, x = mean_surface_area, color = as.factor(Spore_level)))+
  labs (y = "feeding rate", x = "mean_surface_area") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)



```


```{r  feeding rate and initial size (length), echo = FALSE}
filtered_df 
ggplot(filtered_df)+
  geom_point(aes(y = mean_feeding_rate,  x = mean_init_length))+
  geom_point(aes(y =  mean_feeding_rate, x = mean_init_length, color = as.factor(Spore_level)))+
  labs (y = "feeding rate", x = "mean_init_length") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)

```



```{r  feeding rate and spore yield (sa) 1, echo = FALSE}
filtered_df 
 ggplot(filtered_df)+
  geom_point(aes(x = mean_feeding_rate,  y = spores_ul/mean_final_surface_area))+
  geom_point(aes(x =  mean_feeding_rate, y = spores_ul/mean_final_surface_area, color = as.factor(Spore_level)))+
  labs (x = "feeding rate", y = "spores_ulh") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)


```


```{r  feeding rate and spore yield (sa) 2, echo = FALSE}
filtered_df #%>%
ggplot(filtered_df)+
  geom_point(aes(y = mean_feeding_rate,  x = Spore_level))+
  geom_point(aes(y =  mean_feeding_rate, x = Spore_level, color = as.factor(Spore_level)))+
  labs (y = "feeding rate", y = "Spore_level") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)


```

```{r  feeding rate and spore yield (sa) 3, echo = FALSE}
filtered_df #%>%
ggplot(filtered_df)+
  geom_point(aes(y = mean_feeding_rate/mean_surface_area,  x = Spore_level))+
  geom_point(aes(y =  mean_feeding_rate/mean_surface_area, x = Spore_level, color = as.factor(Spore_level)))+
  labs (y = "feeding rate", y = "Spore_level") +
  theme_bw()+
  theme(axis.text = element_text(size = 16, color = "black"),
        axis.title = element_text(size = 24, color = "black"),
        legend.title = element_blank()) +
  facet_wrap(~ Genotype)


```


```{r feeding_statistics}

library(car)

## Full model
mod1 <- with(filtered_df, lm(mean_feeding_rate ~ Genotype * Spore_level * mean_surface_area))
Anova(mod1, type = 3)
summary.aov(mod1, split = list(Genotype = list("A'45" = 1, "Midland 252" = 2, "Midland 281" = 3, "Standard" = 4)))
omega_sq(mod1) # effect size 

(mod2<-with(filtered_df, lm(mean_feeding_rate ~ Genotype + mean_surface_area)))
Anova(mod2, type = 3)
summary.aov(mod2, split = list(Genotype = list("A'45" = 1, "Midland 252" = 2, "Midland 281" = 3, "Standard" = 4)) )

#check the model
plot(mod2)

#run regression on best model
(mod <- with(filtered_df, lm(mean_feeding_rate ~Genotype + mean_surface_area)))
summary(mod) # r = .42, R2 = .41, p < 0.0001
plot(mod)


#guassian model
(mod_g <- with(filtered_df, glm(mean_feeding_rate ~ Genotype + mean_surface_area, family = gaussian(link = identity))))
summary(mod_g)
plot(mod_g)

#quasipoisson model
(mod_p <- with(filtered_df, glm(mean_feeding_rate~ Genotype + mean_surface_area, family = quasipoisson(link = log))))              
summary(mod_p)

```


```{r statistics}

#####################################################################################
####Does feeding rate and spore level at exposure determine infection prevalance?####
#####################################################################################

summary(feed_inf <-glm(cbind(inf, susc) ~ mean_feeding_rate + Spore_level * Genotype,
                      data = filtered_df,
                      family = binomial))

plot(feed_inf)
anova(feed_inf, test = "Chi")


####################################################################################
####Does feeding rate and spore level at exposure determine infection intensity?####
####################################################################################

summary(feed_spore<-glm(spores_ul ~ mean_feeding_rate + mean_final_surface_area + Spore_level + Genotype, 
                        data = filter(filtered_df, spores_ul > 0), 
                        family = Gamma))

plot(feed_spore)
anova(feed_spore, test ="Chi")

```



```{r calculate_treatment_averages, echo = FALSE}
##find averages and se for each Genotype * Spore_level
exp_av <- filtered_df %>%
  arrange(Genotype, Spore_level, Animal, inf) %>%
  filter(inf!= "NaN") %>% 
  group_by(Genotype, Spore_level) %>%
  mutate(n_obs = n()) %>%
  mutate(fr = mean(mean_feeding_rate, na.rm = T), #average feeding rate
            sc_fr = mean(mean_feeding_rate/mean_surface_area, na.rm = T), #average size corrected feeding rate 
            sd_fr = sd(mean_feeding_rate, na.rm = T), #sd feeding rate
            sd_sc_fr = sd(mean_feeding_rate/mean_surface_area, na.rm = T), # sd size corrected feeding rate
            se_fr = sd_fr/sqrt(n()), #se of feeding rate
            se_sc_fr = sd_sc_fr/sqrt(n()),
            spores = mean(spores_ul/mean_final_surface_area, na.rm = T), # average spores_ul - size-corrected
            spore_count = length(spores_ul), na.rm = T, # count of infected animals
            spore_sd = sd(spores_ul/mean_final_surface_area, na.rm = T), # sd of spores_ul
            spore_se = spore_sd/sqrt(spore_count), # se of spores_ul
            repo = mean(fecundity/mean_final_surface_area, na.rm = T), # size corrected
            repo_sd = sd(fecundity/mean_final_surface_area, na.rm = T),
            repo_se = repo_sd/sqrt(n())) %>%  
 dplyr::select(Genotype, Spore_level, fr, sc_fr, sd_fr, sd_sc_fr, se_fr, se_sc_fr, spores, spore_count, spore_sd, spore_se, repo, repo_sd, repo_se) %>% # keep only the columns we want
  distinct() %>% as.data.frame() # drop duplicates.
exp_av      

# at line 524 I added a dplyr:: because there was a conflict for the select function, so the chunk was throwing an error. In case you have conflicts, you can specify the library first with :: as I did there with dplyr::, to specify from which package you want that command to come
```




```{r plot_of_feeding_averages, echo = FALSE}
# plot using fr averages and se
# 

Feed <- ggplot()+
    geom_point(data = exp_av, mapping = aes(x = Spore_level, y = sc_fr, fill = as.factor(Spore_level)),
               size = 5, pch = 21)+
    scale_fill_manual(values = c("darkcyan", "darkmagenta", "darkorange"))+
    geom_errorbar(data = exp_av, mapping = aes(x = Spore_level, 
                                           ymin = sc_fr - se_sc_fr,
                                           ymax = sc_fr + se_sc_fr),
                  width = 0.2)+
     geom_point(data = exp_av, mapping = aes(x = Spore_level, y = sc_fr, fill = as.factor(Spore_level)),
               size = 5, pch = 21)+
    scale_fill_manual(values = c("darkcyan", "darkmagenta", "darkorange"))+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0, 150, 300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color = "black", fill = "NA", size = 0.5))
    #labs(x = "Exposure spore level", y = "Foraging Rate At Exposure")
Feed
```


```{r statistics}

#####################################################################################
####Does feeding rate and spore level at exposure determine infection prevalance?####
#####################################################################################

summary(feed_inf <-glm(cbind(inf, susc) ~ mean_feeding_rate + Spore_level * Genotype,
                      data = filtered_df,
                      family = binomial))

plot(feed_inf)
anova(feed_inf, test = "Chi")


####################################################################################
####Does feeding rate and spore level at exposure determine infection intensity?####
####################################################################################

summary(feed_spore<-glm(spores_ul ~ mean_feeding_rate + mean_final_surface_area + Spore_level + Genotype, 
                        data = filter(filtered_df, spores_ul > 0), 
                        family = Gamma))

plot(feed_spore)
anova(feed_spore, test ="Chi")

```



```{r calculate_treatment_averages, echo = FALSE}
##find averages and se for each Genotype * Spore_level
exp_av <- filtered_df %>%
  arrange(Genotype, Spore_level, Animal, inf) %>%
  filter(inf!= "NaN") %>% 
  group_by(Genotype, Spore_level) %>%
  mutate(n_obs = n()) %>%
  mutate(fr = mean(mean_feeding_rate, na.rm = T), #average feeding rate
            sc_fr = mean(mean_feeding_rate/mean_surface_area, na.rm = T), #average size corrected feeding rate 
            sd_fr = sd(mean_feeding_rate, na.rm = T), #sd feeding rate
            sd_sc_fr = sd(mean_feeding_rate/mean_surface_area, na.rm = T), # sd size corrected feeding rate
            se_fr = sd_fr/sqrt(n()), #se of feeding rate
            se_sc_fr = sd_sc_fr/sqrt(n()),
            spores = mean(spores_ul/mean_final_surface_area, na.rm = T), # average spores_ul - size-corrected
            spore_count = length(spores_ul), na.rm = T, # count of infected animals
            spore_sd = sd(spores_ul/mean_final_surface_area, na.rm = T), # sd of spores_ul
            spore_se = spore_sd/sqrt(spore_count), # se of spores_ul
            repo = mean(fecundity/mean_final_surface_area, na.rm = T), # size corrected
            repo_sd = sd(fecundity/mean_final_surface_area, na.rm = T),
            repo_se = repo_sd/sqrt(n())) %>%  
 dplyr:: select(Genotype, Spore_level, fr, sc_fr, sd_fr, sd_sc_fr, se_fr, se_sc_fr, spores, spore_count, spore_sd, spore_se, repo, repo_sd, repo_se) %>% # keep only the columns we want
  distinct() %>% as.data.frame() # drop duplicates.
exp_av  

# as before, I added a dplyr:: at line 623 for the selct command
```


```{r explore_PO_data, include = FALSE}
# 
# basic<-lm(Abs ~ Time, data=po_data)
# summary(basic)
# 
# (prelim_plot<-ggplot(po_data, aes(x=Time, y =Abs)) +
#     geom_point() +
#     geom_smooth(method="lm")+
#     theme_classic())
# 
# (color_plot<-ggplot(po_data, aes(x=Time, y =Abs, color=Genotype)) +
#     geom_point()+
#     theme_classic())
# 
# ##testing a general model for everything
# all.glm<-glm(Abs ~ Time + Genotype + Spores + Prop_inf, data=po_data)                      
# summary(all.glm)
# 
# #mixed.lmer<-lmer(Abs ~ Time + (1|Genotype) + Spores, data=po_data)
# #summary(mixed.lmer)
# 
# #plot(mixed.lmer)
# #qqnorm(resid(mixed.lmer))
# #qqline(resid(mixed.lmer))
# 
# #(mm_plot<-ggplot(po_data, aes(x=Time, y=Abs, color=Spores)) +
# #    facet_wrap(~Genotype, nrow= 2) +
# #    geom_point(alpha=0.5) +
# #    theme_classic())
# 
# #### Plots for 4.5 hour time point ####
# 
# #subset the data to only include time "4.5"
# subset(po_data, po_data$Time == "4.5")->po4.5
# 
# ##Does level of exposure and infection status predict the amount of active PO?
# # Thoughts: If an ind. fights off infection they will have high active PO;
# # if an ind. trys to fight off an infection and fails they will have low active PO = resources used elsewhere
# (inf_plot_4.5<-ggplot(subset(po4.5, Genotype != "Control"), aes(x=Spores, y=Prop_inf, color=Abs))+
#     scale_color_gradient(low = "white", high = "darkblue")+
#     theme_classic()+
#     geom_point() +
#     facet_wrap(~Genotype))
# 
# 
# ### Now look at the change in abs which equivalent to the amount of active PO produced ####
# #ADD CHANGE IN ABS (ACTIVE PHENOLOXIDASE)
# initial<-subset(po_data, po_data$Time == 1)
# #calculating the change in absorbance
# delta_po<-po4.5$Abs - initial$Abs
# # multiplying by 1000 to get "activity units" (Mucklow & Ebert, 2003)
# delta_po<-delta_po*1000
# # adding the delta_po values back to dataframe
# initial$delta_po<-delta_po
# 
# ##Does level of exposure and infection status predict the amount of active PO?
# (active_po_plot<-ggplot(subset(initial, Genotype != "Control"), 
#                         aes(x=Spores, y=Prop_inf, 
#                             size=delta_po, color=delta_po))+
#     scale_color_gradient(low = "white", high = "darkblue")+
#     theme_classic()+
#     geom_point() +
#     labs(x="Spore level (spores/ml)", y="Proportion of individuals infected")+
#     facet_wrap(~Genotype))
# 
# ##Another way of looking at the same data 
# ggplot(subset(initial, Genotype != "Control"),aes(x=Spores, y=delta_po, color=Genotype, size=Prop_inf)) + 
#   geom_point() +
#   theme_classic()
# 
# 
# #same as above without Genotype coloring
# ggplot(subset(initial, Genotype != "Control"),aes(x=Spores, y=delta_po, size=Prop_inf)) + 
#   geom_point() +
#   theme_classic()
# 
# ####1/15/20 Clay suggests a ANCOVA for data analysis -- covariate = Prop_inf####
# 
# #with interaction : Proportion infected significant
# fit1<-aov(delta_po ~ Genotype + Spores * Prop_inf, data=subset(initial,Genotype!="Control")) 
# summary(fit1)
# #without interaction : Proportion infected and Genotype significant
# fit2<-aov(delta_po ~ Genotype + Spores + Prop_inf -1 , data=subset(initial,Genotype!="Control")) 
# 
# summary(fit2)
# #No interaction between spore level & proportion of infected individuals
# anova(fit1,fit2) 
# 
# ####The best model?? ####
# 
# summary(lm(delta_po ~ Genotype + Spores + Prop_inf -1, data=subset(initial,Genotype!="Control")))
# # Standard is significantly different than the other genotypes
# # As spore level increases, so does active PO
# # As the number of infected individuals in a sample increase, active PO decreases
# 
# ## All these make sense ^^^
# 
# #increased spores leads to higher active PO (seems to be driven by two points)
# (ggplot(subset(initial, Genotype != "Control"), aes(x=Spores, y=delta_po))+
#     geom_point()+
#     geom_smooth(method="lm")+
#     theme_classic())
# 
# 
# #increased proportion infected leads to lower active PO (seems to be driven by two points)
# (ggplot(subset(initial, Genotype != "Control"), aes(x=Prop_inf, y=delta_po))+
#     geom_point()+
#     geom_smooth(method="lm")+
#     theme_classic())
# 
# # add a binomial line to the figures ^^^^
# # and run binomial glm
# 
```




```{r average_PO_plot, echo = FALSE}
#make average phenoloxidase data 

# po_av <-initial %>%
#   group_by(Genotype, Spores) %>%
#   summarise(av_delta_po = mean(delta_po, na.rm = T), #average active phenoloxidase
#             sd = sd(delta_po, na.rm = T), #sd active phenoloxidase
#             count = length(delta_po), # count per genotype*spore level
#             se= sd/sqrt(count), #se of active phenolxidase
#             inf = mean(Prop_inf, na.rm=T), # average proportion infected
#             sd_inf = sd(Prop_inf, na.rm=T), #sd of proportion infected
#             inf_se = sd_inf/sqrt(count)) %>% 
#   dplyr::select(c(1,2,3,6,7,9))
# 
# 
# 
# PO <-ggplot()+
#     geom_point(subset(po_av, Genotype != 'Control'), mapping=aes(x = Spores, y = av_delta_po),
#                size=5, pch=22)+
#     geom_errorbar(subset(po_av, Genotype != 'Control'), mapping=aes(x = Spores, 
#                                            ymin=av_delta_po-se,
#                                            ymax=av_delta_po+se),
#                   width=0.2)+
#     facet_grid(.~Genotype)+
#     theme_classic()+
#     scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
#     theme(panel.border = element_rect(color="black", fill="NA", size=.5),
#           axis.title.x=element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank(),
#           strip.text.x = element_blank())+
#     labs(x="Exposure spore level", y="Active Phenoloxidase")
```













```{r average_offspring_plot, echo = FALSE}

Repo <- ggplot()+
    geom_point(exp_av, mapping = aes(x = Spore_level, y = repo, fill = as.factor(Spore_level)), 
                                     size = 5, pch = 21)+
    scale_fill_manual(values = c("darkcyan" , "darkmagenta", "darkorange"))+  
    geom_errorbar(exp_av, mapping = aes(x = Spore_level, 
                                           ymin = repo - repo_se,
                                           ymax = repo + repo_se),
                  width = 0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    geom_point(exp_av, mapping = aes(x = Spore_level, y = repo, fill = as.factor(Spore_level)), 
                                     size = 5, pch = 21)+
    scale_fill_manual(values = c( "darkcyan", "darkmagenta", "darkorange"))+ 
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color = "black", fill = "NA", size = 0.5),
          axis.title.x = element_blank(),
          axis.text.x   = element_blank(),
          axis.ticks.x  = element_blank(),
          strip.text.x  = element_blank())+
    labs(x = "Exposure spore level", y = "Mean fecundity")
Repo
```





```{r Figure_1, echo = FALSE}
Feed / PInf / Spore / Repo

ggsave("Figures/figure_1.png", width = 5, height = 8)
```


```{r survival_analyses, echo = FALSE}
#install.packages("car", dependencies = TRUE)
#install.packages("survival", dependencies = TRUE)
#install.packages("flexsurv", dependencies = TRUE)
#install.packages("KMsurv", dependencies = TRUE)
#install.packages("e1071", dependencies = TRUE)
#install.packages("rms", dependencies = TRUE)
#library(dplyr) #in tidyverse

#here the read.csv modifies the names of the csv. Using read_csv instead of read.csv at line fixed the problem!
#sadf <- read_csv("data/Survival_AJV2.csv", header = T, sep = ",")
sadf <- read_csv("data/Survival_AJV2.csv")


sadf <- sadf %>% 
  filter(sex != "M")

summary(sadf)

#fecundity.data = subset(sadf, Total.Offspring!="NA")
#Length1 = subset(sadf, Length.at.Day.7..mm.!="NA")
#Length2 = subset(sadf, Length.at.Day.20..mm.!="NA")
#growth = subset(sadf, Growth!="NA")


sadf  %>%
  mutate(gen.numeric = as.numeric(sadf$Genotype)) 

# link/pair time with censor information (+ means censored (i.e., death was not observed during assay) data)
#library(survival)

attach(sadf)

#join spore level and infection status ( 0 = uninfected, 1 = infected)
sadf$grouped <- with(sadf, interaction(Spore_level, Infected))


recsurv <- survival::Surv(Time.till.death_days.post.exposure, Censured)
recsurv

# survfit fits survival curves with various methods
# Kaplan-Meier is most common, so use that if in doubt

fit.KM <- survival::survfit(recsurv ~ 1, type = "kaplan-meier", conf.type = "log-log")
fit.FM <- survival::survfit(recsurv ~ 1, type = "fleming-harrington", conf.type = "log-log")
fit.FM2<- survival::survfit(recsurv ~ 1, type = "fh2", conf.type = "log-log")

# print restricted mean
# # of events = the # of animals that died
print(fit.KM, print.rmean = TRUE)

# plot cummulative harzard, and other mods as
# what's the percentage of animals that die?
plot(fit.KM, fun = "cumhaz")

# cumulative events (f(y)=1-y)
plot(fit.KM, fun = "event")




#### Survival Analyses ####

par(mfrow = c(2,2))
par(las = 1)

# Now, examine if any of the genotypes differ and by spores
#here I got an error because the genotype in the sadf dataframe is called A45, not A-45. I had corrected this multiple times in the spreadsheet but it must have gotten introduced back in/missed somewhere

geno1 <- with(sadf, subset(sadf, Genotype == "A45"))
attach(geno1)
# added the `` because using read_csv earlier slightly changed the column names, and now you have some spaces in the name, so had to use ``
recA45 <- survival::Surv(`Time till death_days post exposure`, Censured)
fitA45 <- with(geno1, fit <- survival::survfit(recA45 ~ geno1$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fitA45, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "A45", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

# in the dataframe, genotype MID-252 doesn't exists; genotype 
# Midland 252
geno2 <- with(sadf, subset(sadf, Genotype == "Midland 252"))
attach(geno2)

# again, had to use `` and change the time till death.. name
recM252 <-survival::Surv(`Time till death_days post exposure`, Censured)
fit252 <- with(geno2, fit <- survival::survfit(recM252 ~ geno2$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fit252,col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "M252", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

# again, had to change to Midland 281
#geno3 <- with(sadf, subset(sadf, Genotype == "MID-281"))
geno3 <- with(sadf, subset(sadf, Genotype == "Midland 281"))
attach(geno3)
# and again, use the ``
recM281 <- survival::Surv(`Time till death_days post exposure`, Censured)
fit281 <- with(geno3, fit <- survival::survfit(recM281 ~ geno3$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fit281, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "M281", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

geno4 <- with(sadf, subset(sadf, Genotype == "STD"))
attach(geno4)
recSTD <- survival::Surv(`Time till death_days post exposure`, Censured)
fitSTD <- with(geno4, fit <- survival::survfit(recSTD ~ geno4$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fitSTD, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "STD",  xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

```

A45's survival is very affected at the 300 spore level

Midland 252's survival is not affected by exposure level 

Midland 281's survival is affected by exposure level, but very few animals actually got sick


```{r pairwise_analyses_within_spore_level, echo = FALSE}

# Genotypes:
# A'45 == 
# Midland 252 == no PIA 
# Midland 281 ==
# Standard == exhibits PIA and appears to be Tolerant 


library(multcomp)

# define the contrast matrix
# use -1 for the baseline group (Standard) 
# seperate analysis by Spore levels (0, 150, and 300)


# Compare Standard against each other Genotype
cmat <- rbind("A45.v.Std" = c1 <- c(1,0,0,-1),
              "Mid252.v.Std" = c2 <- c(0,1,0,-1),
              "Mid281.v.Std"  = c3 <- c(0,0,1,-1))

cmat

#########################
##### Spore Level 0 #####
#########################

d_0<-subset(animal_mean, Spore_level == 0)


## Are feeding rates different? ##
summary(b1<-glm(sc_fr ~ Genotype, d_0, family = gaussian()))


with(d_0, levels(Genotype))

summary(multcomp::glht(b1, linfct = cmat))
plot(summary(multcomp::glht(b1, linfct = cmat)))


## Is fecundity different? ##

summary(b2<-glm(fecundity ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b2, linfct = cmat))
plot(summary(multcomp::glht(b2, linfct = cmat)))


## Is age at first reproduction different? ##

summary(b3<-glm(age_clutch_1 ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b3, linfct = cmat))
plot(summary(multcomp::glht(b3, linfct = cmat)))


## Is growth different? ##

summary(b4<-glm(growth ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b4, linfct = cmat))
plot(summary(multcomp::glht(b4, linfct = cmat)))



###########################
##### Spore Level 150 #####
###########################

d_150<-subset(animal_mean, Spore_level == 150)


## Are feeding rates different? ##
summary(m1<-glm(sc_fr ~ Genotype, d_150, family = gaussian()))


with(d_150, levels(Genotype))

summary(multcomp::glht(m1, linfct = cmat))
plot(summary(multcomp::glht(m1, linfct = cmat)))


## Is spore yield different? ##

summary(m2<-glm(spores_ul ~ Genotype, d_150, family= gaussian()))


summary(multcomp::glht(m2, linfct = cmat))
plot(summary(multcomp::glht(m2, linfct = cmat)))


## Is fecundity different? ##

summary(m3<-glm(fecundity ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m3, linfct = cmat))
plot(summary(multcomp::glht(m3, linfct = cmat)))


## Is age at first reproduction different? ##

summary(m4<-glm(age_clutch_1 ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m4, linfct = cmat))
plot(summary(multcomp::glht(m4, linfct = cmat)))


## Is growth different? ##

summary(m5<-glm(growth ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m5, linfct = cmat))
plot(summary(multcomp::glht(m5, linfct = cmat)))


###########################
##### Spore Level 300 #####
###########################

d_300<-subset(animal_mean, Spore_level == 300)

## Are feeding rates different? ##
summary(s1<-glm(sc_fr ~ Genotype, d_300, family = gaussian()))


with(d_300, levels(Genotype))

summary(multcomp::glht(s1, linfct = cmat))
plot(summary(multcomp::glht(s1, linfct = cmat)))


## Is spore yield different? ##

summary(s2<-glm(spores_ul ~ Genotype, d_300, family= gaussian()))


summary(multcomp::glht(s2, linfct = cmat))
plot(summary(multcomp::glht(s2, linfct = cmat)))


## Is fecundity different? ##

summary(s3<-glm(fecundity ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s3, linfct = cmat))
plot(summary(multcomp::glht(s3, linfct = cmat)))


## Is age at first reproduction different? ##

summary(s4<-glm(age_clutch_1 ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s4, linfct = cmat))
plot(summary(multcomp::glht(s4, linfct = cmat)))


## Is growth different? ##

summary(s5<-glm(growth ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s5, linfct = cmat))
plot(summary(multcomp::glht(s5, linfct = cmat)))


```




```{r pairwise_analyses_within_genotype, echo = FALSE}

# Spore levels:
# 0 == baseline
# 150
# 300



library(multcomp)

# define the contrast matrix
# use -1 for the baseline group (0) 
# seperate analysis by Genotype (Standard, A45, Mid252, Mid281)


# Compare 0 spores against each other spore level
dmat <- rbind("0v150" = c1 <- c(-1,1,0),
              "0v300" = c2 <- c(-1,0,1),
              "150v300"  = c3 <- c(0,-1,1))

dmat

#########################
####### Standard #######
#########################

b_0<-subset(animal_mean, Genotype == "Standard")


## Are feeding rates different? ##
summary(b1<-glm(sc_fr ~ as.factor(Spore_level), b_0, family = gaussian()))


with(b_0, levels(as.factor(Spore_level)))

summary(multcomp::glht(b1, linfct = dmat))
plot(summary(multcomp::glht(b1, linfct = dmat)))


## Is fecundity different? ##

summary(b2<-glm(fecundity ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b2, linfct = dmat))
plot(summary(multcomp::glht(b2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(b3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b3, linfct = dmat))
plot(summary(multcomp::glht(b3, linfct = dmat)))


## Is growth different? ##

summary(b4<-glm(growth ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b4, linfct = dmat))
plot(summary(multcomp::glht(b4, linfct = dmat)))


#########################
#######    A45    #######
#########################

b_a45<-subset(animal_mean, Genotype == "A'45")


## Are feeding rates different? ##
summary(a1<-glm(sc_fr ~ as.factor(Spore_level), b_a45, family = gaussian()))


with(b_a45, levels(as.factor(Spore_level)))

summary(multcomp::glht(a1, linfct = dmat))
plot(summary(multcomp::glht(a1, linfct = dmat)))


## Is fecundity different? ##

summary(a2<-glm(fecundity ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a2, linfct = dmat))
plot(summary(multcomp::glht(a2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(a3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a3, linfct = dmat))
plot(summary(multcomp::glht(a3, linfct = dmat)))


## Is growth different? ##

summary(a4<-glm(growth ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a4, linfct = dmat))
plot(summary(multcomp::glht(a4, linfct = dmat)))


#################################
#######    Midland 252    #######
#################################

b_m252<-subset(animal_mean, Genotype == "Midland 252")


## Are feeding rates different? ##
summary(m1<-glm(sc_fr ~  as.factor(Spore_level), b_m252, family = gaussian()))


with(b_m252, levels(as.factor(Spore_level)))

summary(multcomp::glht(m1, linfct = dmat))
plot(summary(multcomp::glht(m1, linfct = dmat)))


## Is fecundity different? ##

summary(m2<-glm(fecundity ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m2, linfct = dmat))
plot(summary(multcomp::glht(m2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(m3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m3, linfct = dmat))
plot(summary(multcomp::glht(m3, linfct = dmat)))


## Is growth different? ##

summary(m4<-glm(growth ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m4, linfct = dmat))
plot(summary(multcomp::glht(m4, linfct = dmat)))



#################################
#######    Midland 281    #######
#################################

b_m281<-subset(animal_mean, Genotype == "Midland 281")


## Are feeding rates different? ##
summary(mid1<-glm(sc_fr ~ as.factor(Spore_level), b_m281, family = gaussian()))


with(b_m281, levels(as.factor(Spore_level)))

summary(multcomp::glht(mid1, linfct = dmat))
plot(summary(multcomp::glht(mid1, linfct = dmat)))


## Is fecundity different? ##

summary(mid2<-glm(fecundity ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid2, linfct = dmat))
plot(summary(multcomp::glht(mid2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(mid3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid3, linfct = dmat))
plot(summary(multcomp::glht(mid3, linfct = dmat)))


## Is growth different? ##

summary(mid4<-glm(growth ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid4, linfct = dmat))
plot(summary(multcomp::glht(mid4, linfct = dmat)))
```

Standard: feeding rate, fecundity, first clutch, and growth are signficant different between 0v.150 and 0v.300

A45: first clutch and growth are significantly different between 0v.150 and 0v.300

Midland 252: feeding rate significantly different between 0v.150; fecundity between 0v.150 and 0v.300; first clutch between all of them!; growth between 0v.150 and 0v.300

Midland 281:feeding rate significantly different between 0v.150 and 150v.300; fecundity between 0v.150; first clutch between 0v150 and 0v300; growth between 0v150 and 0v300


