---
title: "script"
author: "APB"
date: "12/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(tidyverse)
library(patchwork)
library(AICcmodavg)
library(bbmle)
library(car)
library(knitr)
library(tidyr)
library(lme4)

#setwd()

####Color Theme####

```




```{r load_data, include=FALSE}

##Feeding Rate data
data<-read.csv("AJV2_6Nov2019_JLH.csv")

#Life table data
life<-read.csv("LifeTable_AJV2_3Dec2019.csv")

#check data
head(data)

head(life)

#merge data together
left_join(data, life, by=c("Genotype", "Spore_level", "Animal", "Infected_Uninfected")) %>%
  mutate(Individual_ID = paste(Genotype, 
                               Spore_level, 
                               Animal, 
                               sep = "_")) %>%
  as.data.frame() -> all.data.joined

names(all.data.joined)

##removing unnecessary columns
drops <- c("Sex.y", "Length_Day_7", "Length_Day_20", "DOB", "Total.Offspring")
all.data.joined<-all.data.joined[ , !(names(all.data.joined) %in% drops)]

colnames(all.data.joined)<-c("Genotype", "Spore_level", "Plate", "Animal", "Sex", "Technical_Replicate", "Fluorometry_Reading", "Length_mm", "Size_mm2", "Final_length_mm", "Final_Size_mm2", "Growth_mm2", "Infected_Uninfected", "Susceptible", "Infected", "Spores_ul", "Total_Fecundity", "Control_Number", "Control_Technical_Replicate", "Control_Fluor_Reading", "USE_Control_Fluor_Reading", "Plate_Control", "Time.till.death.days", "Censured", "Growth_mm", "Age_1st_clutch", "Indivdual_ID")

##Remove males from dataframe
all.female<-subset(all.data.joined, all.data.joined$Sex == "F")
```




```{r load_PO_data, echo =FALSE}
##adding AJ2 active phenoloxidase data
all_po_data<-read.csv("AJ2_PO_for_R.csv", header=TRUE)

##cleaning PO data 

##Removing time point 0
subset(all_po_data, all_po_data$Time !="0")->po_data
##Removing NAs
subset(po_data, po_data$Abs != "na")->po_data
##Making all the data numeric
as.character(po_data$Abs)->po_data$Abs
as.numeric(po_data$Abs)->po_data$Abs
as.character(po_data$Prop_inf)->po_data$Prop_inf
as.numeric(po_data$Prop_inf)->po_data$Prop_inf

####po_data includes:Genotypes (control=PBS), Spores (exposed to), ####
## Sample (sample number), Replicate (2 reps from each sample),
## time (in hours), Abs (absorbance value), and 
## Prop_inf (proportion of infected individuals in the sample)
```




```{r calculate_feeding_rate_means_for_each_individual, include=TRUE}

#### Means of the controls  - these means for each treatment (i.e., plate_control) are then used in the calculation below ####
summary_df <- all.female %>%
  group_by(Plate_Control) %>%
  mutate(Control_mean = mean(USE_Control_Fluor_Reading, na.rm = T)) %>%
  select(Plate_Control, Control_mean) %>%
  distinct() %>% as.data.frame()

#remove extra row
summary_df  <- summary_df[!(summary_df$Plate_Control == ""),]

#match control mean with plate treatment
map = setNames(summary_df$Control_mean,summary_df$Plate_Control)
all.female$Control_mean <- map[as.character(all.female$Plate)]
all.female$Control_mean

v = 10 
## volume, mL
t = 7  
##time, hours
k= all.female$Control_mean/all.female$Fluorometry_Reading 
##difference in feeding compared to control

##calculate feeding rate (Sarnelle and Wilson)
all.female$fr_sw <- log(k) * (v/t)

#calculate mean fluor reading per animal (keep rate > 0)
animal_mean <- all.female %>%
  #keep fr_sw values > 0
  filter(fr_sw > 0) %>%
  #group based on these variables
  group_by(Genotype, Spore_level, Animal, Plate, Control_mean) %>%
  #means based on groups above
  summarise(mean_size_animal = mean(Size_mm2, na.rm = TRUE),
            mean_length_animal = mean(Length_mm, na.rm=TRUE),
            mean_fluor_animal = mean(Fluorometry_Reading, na.rm = TRUE),
            susc = mean(Susceptible, na.rm = TRUE),
            inf = mean(Infected, na.rm = TRUE),
            censured = mean(Censured, na.rm=TRUE),
            spores_ul=mean(Spores_ul, na.rm = TRUE),
            growth = mean(Growth_mm, na.rm = TRUE),
            fecundity = mean(Total_Fecundity, na.rm=TRUE),
            age_clutch_1 = mean(Age_1st_clutch, na.rm=TRUE))
animal_mean

##calcualte feeding rate for each animal
animal_mean$fr_sw<-log(animal_mean$Control_mean/animal_mean$mean_fluor_animal) * (v/t)

##size correcting feeding rate for each animal
animal_mean$sc_fr<-animal_mean$fr_sw/animal_mean$mean_size_animal


```




```{r feeding_and_size, include = FALSE}

#feeding rate and length
with(animal_mean, plot(fr_sw ~ mean_length_animal))
with(animal_mean, cor.test(fr_sw, mean_length_animal)) # r = 0.21 ***

with(animal_mean, plot(log(fr_sw) ~ mean_length_animal)) 
with(animal_mean, cor.test(log(fr_sw), mean_length_animal)) #r =.15 **

summary(with(animal_mean, lm(fr_sw~ mean_length_animal))) # r = 0.045, and R2 = 0.042 ***



#feeding rate and size (length^2)
with(animal_mean, plot(fr_sw ~ mean_size_animal))
with(animal_mean, cor.test(fr_sw, mean_size_animal)) #r=.22 ***

with(animal_mean, plot(log(fr_sw) ~ mean_size_animal)) 
with(animal_mean, cor.test(log(fr_sw), mean_size_animal)) #r =.15 **

summary(with(animal_mean, lm(fr_sw~ mean_size_animal))) # r =  0.049, and R2 = 0.046 ***



#feeding rate and length^3
animal_mean$mean_length_cubed<-(animal_mean$mean_length_animal^3)

with(animal_mean, plot(fr_sw ~ mean_length_cubed))
with(animal_mean, cor.test(fr_sw, mean_length_cubed)) # r = 0.23 ***

with(animal_mean, plot(log(fr_sw) ~mean_length_cubed)) 
with(animal_mean, cor.test(log(fr_sw), mean_length_cubed)) #r =.16 ***

summary(with(animal_mean, lm(fr_sw~ mean_length_cubed))) # r = 0.053, and R2 = 0.049 ***


#### Looking at the feeding data ####
(h <- with(animal_mean, hist(fr_sw)))


```




```{r explore_individual_data, echo = FALSE}
(ggplot(filter(animal_mean, inf != "NaN"), mapping=aes(y=fr_sw, x= Spore_level, color= as.factor(inf)))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_grid(.~Genotype)+
  theme_bw())

library(viridis)
(ggplot(filter(animal_mean, spores_ul != "NaN"), mapping=aes(y=fr_sw, x= Spore_level, color= spores_ul),alpha=0.5)+
  geom_point()+
  scale_color_viridis(option = "C")+
  facet_grid(.~Genotype)+
  theme_bw())
```




```{r explore_life_history_data, echo=FALSE}

#### Growth in length_mm ####
ggplot(animal_mean, mapping=aes(x=as.factor(Spore_level), y=growth, 
                                fill = as.factor(inf)))+
  scale_fill_manual(values=c("grey", "limegreen"))+
  geom_violin()+
  facet_grid(.~Genotype)+
  theme_bw()


#### Total Fecundity ####
ggplot(filter(animal_mean, inf != "NaN"), mapping=aes(x=as.factor(Spore_level), 
                                                      y = fecundity, 
                                                      fill = as.factor(inf)))+
  scale_fill_manual(values=c("grey", "limegreen"))+
  geom_violin()+
  facet_grid(.~Genotype)+
  theme_bw()


#### Age at First Clutch ####
ggplot(filter(animal_mean, inf != "NaN"), mapping=aes(x=as.factor(Spore_level), 
                                                      y = age_clutch_1, 
                                                      fill = as.factor(inf)))+
  scale_fill_manual(values=c("grey", "limegreen"))+
  geom_violin()+
  facet_grid(.~Genotype)+
  theme_bw()

ggplot(filter(animal_mean, inf != "NaN"), mapping=aes(x=as.factor(Spore_level), 
                                                      y = age_clutch_1, 
                                                      color = as.factor(inf)))+
  scale_color_manual(values=c("grey", "limegreen"))+
  geom_boxplot()+
  facet_grid(.~Genotype)+
  theme_classic()+
  theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank())

```



```{r feeding_statistics}

## Full model
(mod1 <- with(animal_mean, aov(fr_sw ~ Genotype + Spore_level + mean_size_animal)))
Anova(mod1, type = 3)
summary.aov(mod1, split = list(Genotype = list("A'45" = 1, "Midland 252" = 2, "Midland 281" = 3, "Standard" = 4)))
omega_sq(mod1) # effect size 

(mod2<-with(animal_mean, aov(fr_sw ~Genotype + mean_size_animal)))
Anova(mod2, type = 3)
summary.aov(mod2, split = list(Genotype = list("A'45" = 1, "Midland 252" = 2, "Midland 281" = 3, "Standard" = 4)) )

#check the model
plot(mod2)

#run regression on best model
(mod <- with(animal_mean, lm(fr_sw ~Genotype + mean_size_animal)))
summary(mod) # r = .42, R2 = .41, p < 0.0001
plot(mod)


#guassian model
(mod_g <- with(animal_mean, glm(fr_sw ~Genotype + mean_size_animal, family = gaussian(link = identity))))
summary(mod_g)
plot(mod_g)

#quasipoisson model
(mod_p <- with(animal_mean, glm(fr_sw ~Genotype + mean_size_animal, family = quasipoisson(link = log))))              
summary(mod_p)

```



```{r statistics}

#####################################################################################
####Does feeding rate and spore level at exposure determine infection prevalance?####
#####################################################################################

summary(feed_inf<-glm(cbind(inf, susc) ~ fr_sw + Spore_level + Genotype,
                      data=animal_mean,
                      family=binomial))

plot(feed_inf)
anova(feed_inf, test="Chi")


####################################################################################
####Does feeding rate and spore level at exposure determine infection intensity?####
####################################################################################

summary(feed_spore<-glm(spores_ul ~ fr_sw + mean_size_animal + Spore_level + Genotype, 
                        data=filter(animal_mean, spores_ul > 0), 
                        family=Gamma))

plot(feed_spore)
anova(feed_spore, test ="Chi")

```




```{r calculate_treatment_averages, echo = FALSE}
##find averages and se for each Genotype * Spore_level
exp_av<-animal_mean %>%
  group_by(Genotype, Spore_level, inf) %>%
  summarise(fr = mean(fr_sw, na.rm = T), #average feeding rate
            av_fr = mean(sc_fr, na.rm=T), #average size corrected feeding rate 
            sd = sd(fr_sw, na.rm = T), #sd feeding rate
            sd_fr = sd(sc_fr, na.rm=T), # sd size corrected feeding rate
            count = length(sc_fr), # count per genotype*spore level
            se= sd/sqrt(count), #se of feeding rate
            se_fr = sd_fr/sqrt(count), # se of size corrected feeding rate
            spores = mean(spores_ul, na.rm=T), # average spores_ul
            spore_count = length(spores_ul), na.rm=T, # count of infected animals
            spore_sd = sd(spores_ul, na.rm=T), # sd of spores_ul
            spore_se = spore_sd/sqrt(spore_count), # se of spores_ul
            repo = mean(fecundity, na.rm=T),
            repo_sd = sd(fecundity, na.rm=T),
            repo_se = repo_sd/sqrt(count)) %>%  
   dplyr::select(c(1,2,3,4,5,9, 10, 11,15,16,18)) 

#remove the NAs in inf
exp_av<-filter(exp_av, inf != "NaN")

```




```{r plot_of_feeding_averages, echo = FALSE}
#plot using size corrected averages and se

(ggplot()+
    geom_point(data=exp_av, mapping=aes(x=Spore_level, y=av_fr, fill=as.factor(inf)),
               size=5, pch=22)+
    scale_fill_manual(values=c("grey", "limegreen"))+
    geom_errorbar(data=exp_av, mapping=aes(x=Spore_level, 
                                           ymin=av_fr-se_fr,
                                           ymax=av_fr+se_fr),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5))+
    labs(x="Exposure spore level", y="Foraging Rate At Exposure"))


#plot using averages and se

Feed<-ggplot()+
    geom_point(data=exp_av, mapping=aes(x=Spore_level, y=fr, fill=as.factor(inf)),
               size=5, pch=22)+
    scale_fill_manual(values=c("grey", "limegreen"))+
    geom_errorbar(data=exp_av, mapping=aes(x=Spore_level, 
                                           ymin=fr-se,
                                           ymax=fr+se),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          legend.position = "none")+
    labs(x="Exposure spore level", y="Feeding Rate")

```




```{r explore_PO_data, include = FALSE}

basic<-lm(Abs ~ Time, data=po_data)
summary(basic)

(prelim_plot<-ggplot(po_data, aes(x=Time, y =Abs)) +
    geom_point() +
    geom_smooth(method="lm")+
    theme_classic())

(color_plot<-ggplot(po_data, aes(x=Time, y =Abs, color=Genotype)) +
    geom_point()+
    theme_classic())

##testing a general model for everything
all.glm<-glm(Abs ~ Time + Genotype + Spores + Prop_inf, data=po_data)                      
summary(all.glm)

#mixed.lmer<-lmer(Abs ~ Time + (1|Genotype) + Spores, data=po_data)
#summary(mixed.lmer)

#plot(mixed.lmer)
#qqnorm(resid(mixed.lmer))
#qqline(resid(mixed.lmer))

#(mm_plot<-ggplot(po_data, aes(x=Time, y=Abs, color=Spores)) +
#    facet_wrap(~Genotype, nrow= 2) +
#    geom_point(alpha=0.5) +
#    theme_classic())

#### Plots for 4.5 hour time point ####

#subset the data to only include time "4.5"
subset(po_data, po_data$Time == "4.5")->po4.5

##Does level of exposure and infection status predict the amount of active PO?
# Thoughts: If an ind. fights off infection they will have high active PO;
# if an ind. trys to fight off an infection and fails they will have low active PO = resources used elsewhere
(inf_plot_4.5<-ggplot(subset(po4.5, Genotype != "Control"), aes(x=Spores, y=Prop_inf, color=Abs))+
    scale_color_gradient(low = "white", high = "darkblue")+
    theme_classic()+
    geom_point() +
    facet_wrap(~Genotype))


### Now look at the change in abs which equivalent to the amount of active PO produced ####
#ADD CHANGE IN ABS (ACTIVE PHENOLOXIDASE)
initial<-subset(po_data, po_data$Time == 1)
#calculating the change in absorbance
delta_po<-po4.5$Abs - initial$Abs
# multiplying by 1000 to get "activity units" (Mucklow & Ebert, 2003)
delta_po<-delta_po*1000
# adding the delta_po values back to dataframe
initial$delta_po<-delta_po

##Does level of exposure and infection status predict the amount of active PO?
(active_po_plot<-ggplot(subset(initial, Genotype != "Control"), 
                        aes(x=Spores, y=Prop_inf, 
                            size=delta_po, color=delta_po))+
    scale_color_gradient(low = "white", high = "darkblue")+
    theme_classic()+
    geom_point() +
    labs(x="Spore level (spores/ml)", y="Proportion of individuals infected")+
    facet_wrap(~Genotype))

##Another way of looking at the same data 
ggplot(subset(initial, Genotype != "Control"),aes(x=Spores, y=delta_po, color=Genotype, size=Prop_inf)) + 
  geom_point() +
  theme_classic()


#same as above without Genotype coloring
ggplot(subset(initial, Genotype != "Control"),aes(x=Spores, y=delta_po, size=Prop_inf)) + 
  geom_point() +
  theme_classic()

####1/15/20 Clay suggests a ANCOVA for data analysis -- covariate = Prop_inf####

#with interaction : Proportion infected significant
fit1<-aov(delta_po ~ Genotype + Spores * Prop_inf, data=subset(initial,Genotype!="Control")) 
summary(fit1)
#without interaction : Proportion infected and Genotype significant
fit2<-aov(delta_po ~ Genotype + Spores + Prop_inf -1 , data=subset(initial,Genotype!="Control")) 

summary(fit2)
#No interaction between spore level & proportion of infected individuals
anova(fit1,fit2) 

####The best model?? ####

summary(lm(delta_po ~ Genotype + Spores + Prop_inf -1, data=subset(initial,Genotype!="Control")))
# Standard is significantly different than the other genotypes
# As spore level increases, so does active PO
# As the number of infected individuals in a sample increase, active PO decreases

## All these make sense ^^^

#increased spores leads to higher active PO (seems to be driven by two points)
(ggplot(subset(initial, Genotype != "Control"), aes(x=Spores, y=delta_po))+
    geom_point()+
    geom_smooth(method="lm")+
    theme_classic())


#increased proportion infected leads to lower active PO (seems to be driven by two points)
(ggplot(subset(initial, Genotype != "Control"), aes(x=Prop_inf, y=delta_po))+
    geom_point()+
    geom_smooth(method="lm")+
    theme_classic())

# add a binomial line to the figures ^^^^
# and run binomial glm

```




```{r average_PO_plot, echo = FALSE}
#make average phenoloxidase data 

po_av<-initial %>%
  group_by(Genotype, Spores) %>%
  summarise(av_delta_po = mean(delta_po, na.rm = T), #average active phenoloxidase
            sd = sd(delta_po, na.rm = T), #sd active phenoloxidase
            count = length(delta_po), # count per genotype*spore level
            se= sd/sqrt(count), #se of active phenolxidase
            inf = mean(Prop_inf, na.rm=T), # average proportion infected
            sd_inf = sd(Prop_inf, na.rm=T), #sd of proportion infected
            inf_se = sd_inf/sqrt(count)) %>% 
  dplyr::select(c(1,2,3,6,7,9))



PO<-ggplot()+
    geom_point(subset(po_av, Genotype != 'Control'), mapping=aes(x=Spores, y=av_delta_po),
               size=5, pch=22)+
    geom_errorbar(subset(po_av, Genotype != 'Control'), mapping=aes(x=Spores, 
                                           ymin=av_delta_po-se,
                                           ymax=av_delta_po+se),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          strip.text.x = element_blank())+
    labs(x="Exposure spore level", y="Active Phenoloxidase")
```




```{r percent_infected_plot, echo = FALSE}
#find the percent infected per Genotype and Spore level

infection<-animal_mean %>%
  group_by(Genotype, Spore_level) %>%
  summarise(infected = mean(inf, na.rm = T), #average infected
            sd = sd(inf, na.rm = T), #sd infected
            count = length(inf), # count per genotype*spore level
            se= sd/sqrt(count)) %>%#se of infected 
  dplyr::select(c(1,2,3,6))

# make figure

PInf<-ggplot()+
    geom_point(infection, mapping=aes(x=Spore_level, y=infected),
               size=5, pch=22)+
    geom_errorbar(infection, mapping=aes(x=Spore_level, 
                                           ymin=infected-se,
                                           ymax=infected+se),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank(),
         strip.text.x = element_blank())+
    labs(y="Percent Infected")

```




```{r spore_yield_plot, echo = FALSE}

Spore<-ggplot()+
    geom_point(subset(exp_av, inf == 1), mapping=aes(x=Spore_level, y=spores),size=5, pch=22)+
    geom_errorbar(subset(exp_av, inf == 1), mapping=aes(x=Spore_level, 
                                           ymin=spores-spore_se,
                                           ymax=spores+spore_se),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank(),
         strip.text.x = element_blank())+
    labs(x="Exposure spore level", y="Spore Yield (spores/ul)")

```




```{r spore_yield_plot, echo = FALSE}

Repo<-ggplot()+
    geom_point(exp_av, mapping=aes(x=Spore_level, y=repo, fill = as.factor(inf)),size=5, pch=22)+
    geom_errorbar(exp_av, mapping=aes(x=Spore_level, 
                                           ymin=repo-repo_se,
                                           ymax=repo+repo_se),
                  width=0.2)+
    facet_grid(.~Genotype)+
    theme_classic()+
    scale_fill_manual(values=c("grey", "limegreen"))+
    scale_x_continuous(breaks = c(0,150,300), limits = c(-20, 320))+
    theme(panel.border = element_rect(color="black", fill="NA", size=.5),
          strip.text.x = element_blank(),
          legend.position = "none")+
    labs(x="Exposure spore level", y="Average Offspring")

```





```{r Figure_1, echo = FALSE}
Feed / PO / PInf / Spore / Repo
```



```{r survival_analyses, echo = FALSE}
#install.packages("car", dependencies = TRUE)
#install.packages("survival", dependencies = TRUE)
#install.packages("flexsurv", dependencies = TRUE)
#install.packages("KMsurv", dependencies = TRUE)
#install.packages("e1071", dependencies = TRUE)
#install.packages("rms", dependencies = TRUE)
#library(dplyr) #in tidyverse

sadf <- read.csv("Survival_AJV2.csv", header = T, sep = ",")
sadf <- sadf[!(sadf$Sex == "M"),]
summary(sadf)

fecundity.data = subset(sadf, Total.Offspring!="NA")
Length1 = subset(sadf, Length.at.Day.7..mm.!="NA")
Length2 = subset(sadf, Length.at.Day.20..mm.!="NA")
growth = subset(sadf, Growth!="NA")

sadf  %>%
  mutate(gen.numeric = as.numeric(sadf$Genotype)) 

# link/pair time with censor information (+ means censored (i.e., death was not observed during assay) data)
#library(survival)

attach(sadf)

recsurv <- survival::Surv(Time.till.death_days.post.exposure,Censured)
recsurv

# survfit fits survival curves with various methods
# Kaplan-Meier is most common, so use that if in doubt

fit.KM <- survival::survfit(recsurv ~ 1, type = "kaplan-meier", conf.type = "log-log")
fit.FM <- survival::survfit(recsurv ~ 1, type = "fleming-harrington", conf.type = "log-log")
fit.FM2<- survival::survfit(recsurv ~ 1, type = "fh2", conf.type = "log-log")

# print restricted mean
# # of events = the # of animals that died
print(fit.KM, print.rmean = TRUE)

# plot cummulative harzard, and other mods as
# what's the percentage of animals that die?
plot(fit.KM, fun = "cumhaz")

# cumulative events (f(y)=1-y)
plot(fit.KM, fun = "event")




#### Survival Analyses ####

par(mfrow = c(2,2))
par(las = 1)

# Now, examine if any of the genotypes differ and by spores
geno1 <- with(sadf, subset(sadf, Genotype == "A-45"))
attach(geno1)
recA45 <- survival::Surv(Time.till.death_days.post.exposure, Censured)
fitA45 <- with(geno1, fit <- survival::survfit(recA45 ~ as.numeric(geno1$Spore_level), type = "kaplan-meier", conf.type = "log-log"))
plot(fitA45, col = c("darkcyan", "darkmagenta","black"), main = "A45", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150", "300"),  lty = 1, bty  ='n', col = c("darkcyan", "darkmagenta","black"), cex = 0.90)

geno2 <- with(sadf, subset(sadf, Genotype == "MID-252"))
attach(geno2)
recM252 <-survival::Surv(Time.till.death_days.post.exposure, Censured)
fit252 <- with(geno2, fit <- survival::survfit(recM252 ~ as.numeric(geno2$Spore_level), type = "kaplan-meier", conf.type = "log-log"))
plot(fit252,col = c("darkcyan", "darkmagenta","black"), main = "M252", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150", "300"),  lty = 1, bty  ='n', col = c("darkcyan", "darkmagenta","black"), cex = 0.90)

geno3 <- with(sadf, subset(sadf, Genotype == "MID-281"))
attach(geno3)
recM281 <- survival::Surv(Time.till.death_days.post.exposure, Censured)
fit281 <- with(geno3, fit <- survival::survfit(recM281 ~ as.numeric(geno3$Spore_level), type = "kaplan-meier", conf.type = "log-log"))
plot(fit281, col = c("darkcyan", "darkmagenta","black"), main = "M281", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150", "300"),  lty = 1, bty  ='n', col = c("darkcyan", "darkmagenta","black"), cex = 0.90)

geno4 <- with(sadf, subset(sadf, Genotype == "STD"))
attach(geno4)
recSTD <- survival::Surv(Time.till.death_days.post.exposure, Censured)
fitSTD <- with(geno4, fit <- survival::survfit(recSTD ~ as.numeric(geno4$Spore_level),type = "kaplan-meier", conf.type = "log-log"))
plot(fitSTD, col = c("darkcyan", "darkmagenta","black"), main = "STD",  xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150", "300"),  lty = 1, bty  ='n', col = c("darkcyan", "darkmagenta","black"), cex = 0.90)

```
A45's survival is very affected at the 300 spore level

Midland 252's survival is not affected by exposure level 

Midland 281's survival is affected by exposure level, but very few animals actually got sick



```{r pairwise_analyses_within_spore_level, echo = FALSE}

# Genotypes:
# A'45 == 
# Midland 252 == no PIA 
# Midland 281 ==
# Standard == exhibits PIA and appears to be Tolerant 


library(multcomp)

# define the contrast matrix
# use -1 for the baseline group (Standard) 
# seperate analysis by Spore levels (0, 150, and 300)


# Compare Standard against each other Genotype
cmat <- rbind("A45.v.Std" = c1 <- c(1,0,0,-1),
              "Mid252.v.Std" = c2 <- c(0,1,0,-1),
              "Mid281.v.Std"  = c3 <- c(0,0,1,-1))

cmat

#########################
##### Spore Level 0 #####
#########################

d_0<-subset(animal_mean, Spore_level == 0)


## Are feeding rates different? ##
summary(b1<-glm(sc_fr ~ Genotype, d_0, family = gaussian()))


with(d_0, levels(Genotype))

summary(multcomp::glht(b1, linfct = cmat))
plot(summary(multcomp::glht(b1, linfct = cmat)))


## Is fecundity different? ##

summary(b2<-glm(fecundity ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b2, linfct = cmat))
plot(summary(multcomp::glht(b2, linfct = cmat)))


## Is age at first reproduction different? ##

summary(b3<-glm(age_clutch_1 ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b3, linfct = cmat))
plot(summary(multcomp::glht(b3, linfct = cmat)))


## Is growth different? ##

summary(b4<-glm(growth ~ Genotype, d_0, family = gaussian()))

summary(multcomp::glht(b4, linfct = cmat))
plot(summary(multcomp::glht(b4, linfct = cmat)))



###########################
##### Spore Level 150 #####
###########################

d_150<-subset(animal_mean, Spore_level == 150)


## Are feeding rates different? ##
summary(m1<-glm(sc_fr ~ Genotype, d_150, family = gaussian()))


with(d_150, levels(Genotype))

summary(multcomp::glht(m1, linfct = cmat))
plot(summary(multcomp::glht(m1, linfct = cmat)))


## Is spore yield different? ##

summary(m2<-glm(spores_ul ~ Genotype, d_150, family= gaussian()))


summary(multcomp::glht(m2, linfct = cmat))
plot(summary(multcomp::glht(m2, linfct = cmat)))


## Is fecundity different? ##

summary(m3<-glm(fecundity ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m3, linfct = cmat))
plot(summary(multcomp::glht(m3, linfct = cmat)))


## Is age at first reproduction different? ##

summary(m4<-glm(age_clutch_1 ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m4, linfct = cmat))
plot(summary(multcomp::glht(m4, linfct = cmat)))


## Is growth different? ##

summary(m5<-glm(growth ~ Genotype, d_150, family = gaussian()))

summary(multcomp::glht(m5, linfct = cmat))
plot(summary(multcomp::glht(m5, linfct = cmat)))


###########################
##### Spore Level 300 #####
###########################

d_300<-subset(animal_mean, Spore_level == 300)

## Are feeding rates different? ##
summary(s1<-glm(sc_fr ~ Genotype, d_300, family = gaussian()))


with(d_300, levels(Genotype))

summary(multcomp::glht(s1, linfct = cmat))
plot(summary(multcomp::glht(s1, linfct = cmat)))


## Is spore yield different? ##

summary(s2<-glm(spores_ul ~ Genotype, d_300, family= gaussian()))


summary(multcomp::glht(s2, linfct = cmat))
plot(summary(multcomp::glht(s2, linfct = cmat)))


## Is fecundity different? ##

summary(s3<-glm(fecundity ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s3, linfct = cmat))
plot(summary(multcomp::glht(s3, linfct = cmat)))


## Is age at first reproduction different? ##

summary(s4<-glm(age_clutch_1 ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s4, linfct = cmat))
plot(summary(multcomp::glht(s4, linfct = cmat)))


## Is growth different? ##

summary(s5<-glm(growth ~ Genotype, d_300, family = gaussian()))

summary(multcomp::glht(s5, linfct = cmat))
plot(summary(multcomp::glht(s5, linfct = cmat)))


```




```{r pairwise_analyses_within_genotype, echo = FALSE}

# Spore levels:
# 0 == baseline
# 150
# 300



library(multcomp)

# define the contrast matrix
# use -1 for the baseline group (0) 
# seperate analysis by Genotype (Standard, A45, Mid252, Mid281)


# Compare 0 spores against each other spore level
dmat <- rbind("0v150" = c1 <- c(-1,1,0),
              "0v300" = c2 <- c(-1,0,1),
              "150v300"  = c3 <- c(0,-1,1))

dmat

#########################
####### Standard #######
#########################

b_0<-subset(animal_mean, Genotype == "Standard")


## Are feeding rates different? ##
summary(b1<-glm(sc_fr ~ as.factor(Spore_level), b_0, family = gaussian()))


with(b_0, levels(as.factor(Spore_level)))

summary(multcomp::glht(b1, linfct = dmat))
plot(summary(multcomp::glht(b1, linfct = dmat)))


## Is fecundity different? ##

summary(b2<-glm(fecundity ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b2, linfct = dmat))
plot(summary(multcomp::glht(b2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(b3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b3, linfct = dmat))
plot(summary(multcomp::glht(b3, linfct = dmat)))


## Is growth different? ##

summary(b4<-glm(growth ~ as.factor(Spore_level), b_0, family = gaussian()))

summary(multcomp::glht(b4, linfct = dmat))
plot(summary(multcomp::glht(b4, linfct = dmat)))


#########################
#######    A45    #######
#########################

b_a45<-subset(animal_mean, Genotype == "A'45")


## Are feeding rates different? ##
summary(a1<-glm(sc_fr ~ as.factor(Spore_level), b_a45, family = gaussian()))


with(b_a45, levels(as.factor(Spore_level)))

summary(multcomp::glht(a1, linfct = dmat))
plot(summary(multcomp::glht(a1, linfct = dmat)))


## Is fecundity different? ##

summary(a2<-glm(fecundity ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a2, linfct = dmat))
plot(summary(multcomp::glht(a2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(a3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a3, linfct = dmat))
plot(summary(multcomp::glht(a3, linfct = dmat)))


## Is growth different? ##

summary(a4<-glm(growth ~ as.factor(Spore_level), b_a45, family = gaussian()))

summary(multcomp::glht(a4, linfct = dmat))
plot(summary(multcomp::glht(a4, linfct = dmat)))


#################################
#######    Midland 252    #######
#################################

b_m252<-subset(animal_mean, Genotype == "Midland 252")


## Are feeding rates different? ##
summary(m1<-glm(sc_fr ~  as.factor(Spore_level), b_m252, family = gaussian()))


with(b_m252, levels(as.factor(Spore_level)))

summary(multcomp::glht(m1, linfct = dmat))
plot(summary(multcomp::glht(m1, linfct = dmat)))


## Is fecundity different? ##

summary(m2<-glm(fecundity ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m2, linfct = dmat))
plot(summary(multcomp::glht(m2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(m3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m3, linfct = dmat))
plot(summary(multcomp::glht(m3, linfct = dmat)))


## Is growth different? ##

summary(m4<-glm(growth ~ as.factor(Spore_level), b_m252, family = gaussian()))

summary(multcomp::glht(m4, linfct = dmat))
plot(summary(multcomp::glht(m4, linfct = dmat)))



#################################
#######    Midland 281    #######
#################################

b_m281<-subset(animal_mean, Genotype == "Midland 281")


## Are feeding rates different? ##
summary(mid1<-glm(sc_fr ~ as.factor(Spore_level), b_m281, family = gaussian()))


with(b_m281, levels(as.factor(Spore_level)))

summary(multcomp::glht(mid1, linfct = dmat))
plot(summary(multcomp::glht(mid1, linfct = dmat)))


## Is fecundity different? ##

summary(mid2<-glm(fecundity ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid2, linfct = dmat))
plot(summary(multcomp::glht(mid2, linfct = dmat)))


## Is age at first reproduction different? ##

summary(mid3<-glm(age_clutch_1 ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid3, linfct = dmat))
plot(summary(multcomp::glht(mid3, linfct = dmat)))


## Is growth different? ##

summary(mid4<-glm(growth ~ as.factor(Spore_level), b_m281, family = gaussian()))

summary(multcomp::glht(mid4, linfct = dmat))
plot(summary(multcomp::glht(mid4, linfct = dmat)))
```

Standard: feeding rate, fecundity, first clutch, and growth are signficant different between 0v.150 and 0v.300

A45: first clutch and growth are significantly different between 0v.150 and 0v.300

Midland 252: feeding rate significantly different between 0v.150; fecundity between 0v.150 and 0v.300; first clutch between all of them!; growth between 0v.150 and 0v.300

Midland 281:feeding rate significantly different between 0v.150 and 150v.300; fecundity between 0v.150; first clutch between 0v150 and 0v300; growth between 0v150 and 0v300