---
title: "Appendix"
author: "APB"
date: "7/23/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load libraries, include = FALSE, warning = FALSE, message = FALSE}
devtools::install_github("zeehio/facetscales")
library(ggplot2)
library(patchwork)
library(tidyverse)
library(cowplot)  
library(here)
library(facetscales)
require(facetscales)
library(lme4)
#library(countreg)
library(MASS)
library(pscl)
library(flextable)
library(betareg)
library(emmeans)
library(survival)
```

# Comparison of spore counts using flow cytometry to traditional counts using a hemocytometer in 'Standard' genotype
```{r spore_check, echo = FALSE}
sporecheck<-read.csv(here("01_Data", "Alaina_counted_Standard_spores.csv"))

sporecheck %>%
  ggplot(mapping=aes(x=sp.ul, y = flow_sp_ul))+
  geom_point()+
  geom_smooth(method= "lm")+
  labs(x = "Spore yield counted by eye (sp/ul)", y = "Spore yield measured using Flow Cytometry (sp/ul)")
```

```{r}
fit<-lm(sp.ul ~ flow_sp_ul - 1, data = sporecheck) 
# R squared
summary(fit)$r.squared
```

## Survival Analyses
```{r survival, echo = FALSE}

#### Survival Analyses ####

# Now, examine if any of the genotypes differ and by spores
inf1<-readRDS("inf1.RDS")
inf1$grouped <- with(inf1, interaction(Spore_level, Infected_Uninfected))

#A45
geno1 <- with(inf1, subset(inf1, Genotype == "A45"))
attach(geno1)

recA45 <- survival::Surv(meandaydeath, censored)
fitA45 <- with(geno1, fit <- survival::survfit(recA45 ~ geno1$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fitA45, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "A45", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

# Midland 252
geno2 <- with(inf1, subset(inf1, Genotype == "Midland 252"))
attach(geno2)

recM252 <-survival::Surv(meandaydeath, censored)
fit252 <- with(geno2, fit <- survival::survfit(recM252 ~ geno2$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fit252,col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "Midland 252", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
```

## Survival Analyses Continued
```{r continued, echo = FALSE}
#Midland 281
geno3 <- with(inf1, subset(inf1, Genotype == "Midland 281"))
attach(geno3)

recM281 <- survival::Surv(meandaydeath, censored)
fit281 <- with(geno3, fit <- survival::survfit(recM281 ~ geno3$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fit281, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "Midland 281", xlab= "Days since exposure", ylab = "Survival", ylim= range(0.5,1))
legend(x = 'bottomleft', c("0", "150 Uninfected", "150 Infected", "300 Uninfected", "300 Infected"),  lty = 1, bty  ='n', col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), cex = 0.90)

#Standard
geno4 <- with(inf1, subset(inf1, Genotype == "Standard"))
attach(geno4)

recSTD <- survival::Surv(meandaydeath, censored)
fitSTD <- with(geno4, fit <- survival::survfit(recSTD ~ geno4$grouped, type = "kaplan-meier", conf.type = "log-log"))
plot(fitSTD, col = c("darkcyan", "cyan", "darkmagenta", "magenta", "black"), main = "Standard",  xlab= "Days since exposure", ylab = "Survival")
```
In Standard, there was only one individual that was exposed to 150 sp/ml that did not get infected and that individual died eleven days after the exposure (blue line). 

## Impacts of Feeding Behavior
```{r plotting feeding rates and host longevity (mean day of death),  echo = FALSE}
inf3<-readRDS('inf3.RDS')

plotlifespan <- inf3 %>% 
  ggplot(aes(y = meandaydeath, 
             x = meanfeedrate, 
             ymin = meandaydeath - sedeathday,
             ymax = meandaydeath + sedeathday, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  #geom_point(position = position_dodge(0.2), size = 2)+
  geom_errorbar(aes(ymin = meandaydeath - sedeathday,
                    ymax = meandaydeath + sedeathday,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 4) +
  ylab("Lifespan (mean day of death)") + 
  labs(x = expression("LN Feeding rate (mL"^-1* ind^-1* hr^-1*")")) +
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))+
  theme(legend.position = "none")
  #labs(shape = "Pathogen dose", color = "Host genotype") 
plotlifespan

plotdayfirstclutch <- inf3 %>% 
  ggplot(aes(y = meandayfirstclutch, 
             x = meanfeedrate, 
             ymin = meandayfirstclutch - sefirstclutch,
             ymax = meandayfirstclutch + sefirstclutch, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  geom_point(position = position_dodge(0.2), size = 2)+
  geom_errorbar(aes(ymin = meandayfirstclutch - sefirstclutch,
                    ymax = meandayfirstclutch + sefirstclutch,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 4) +
  ylab("Day of first reproduction") + 
  labs(x = expression("LN Feeding rate (mL"^-1* ind^-1* hr^-1*")")) +
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 

plotdayfirstclutch
```

\newpage
## Impacts of Infection
```{r plotting spore yield (within-host pathogen density) and host growth,  echo = FALSE}
plotgrowthyield <- inf3 %>% 
  ggplot(aes(y = meanspores, 
             x = meangrowth, 
             ymin = meanspores - sespores,
             ymax = meanspores + sespores, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  geom_point(position = position_dodge(0.2), size = 5)+
  geom_errorbar(aes(ymin = meanspores - sespores,
                    ymax = meanspores + sespores,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meangrowth - segrowth, 
                     xmax = meangrowth + segrowth,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 5) +
  labs(y = expression("Spore yield (spores host"^-1* "x 10"^3* ")"))+ 
  labs(x = expression("Total growth (final - initial size, mm"^2*")")) +
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "none")
plotgrowthyield 

plotfityield <- inf3 %>% 
  ggplot(aes(x = meanspores, 
             y = meanfitnes, 
             xmin = meanspores - sespores,
             xmax = meanspores + sespores, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  geom_point(position = position_dodge(0.2), size = 5)+
  geom_errorbarh(aes(xmin = meanspores - sespores,
                     xmax = meanspores + sespores,
                     height = 0)) +
  geom_errorbar(aes(ymin = meanfitnes - sefitness, 
                    ymax = meanfitnes + sefitness,
                    width = 0)) +
  geom_point(position = position_dodge(0.2), size = 5) +
  labs(x = expression("Spore yield (spores host"^-1* " 10"^3* ")"))+ 
  labs(y = expression("Total reproduction (host" ^-1*")")) +
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
plotfityield
```


