---
title: "Pfenning-ButterworthFiguresandStats"
output:
  pdf_document: default
  html_document: default
  word_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r test, warning = FALSE}
   withCallingHandlers(
        expr    = as.numeric(c("1", "A")), 
        warning = function(w) warn <<- paste("** warning:", w$message, "**\n\n")
   )
```

```{r print_warn, echo=FALSE}
  if(exists("warn")) cat(warn)
```

Load libraries

```{r load libraries, include = FALSE, warning = FALSE, message = FALSE}
devtools::install_github("zeehio/facetscales")
library(ggplot2)
library(patchwork)
library(tidyverse)
library(ggpmisc)
library(cowplot)  
library(here)
library(facetscales)
library(lme4)
#library(countreg)
library(MASS)
library(pscl)
library(flextable)
library(betareg)
library(emmeans)
library(survival)
library(bbmle)
library(car)
```

```{r load data, include = FALSE, echo = FALSE}
df <- read.csv(here("01_Data", "MeansForFeedingRateAJV2.csv"))
names(df)

with(df, hist(mean_feeding_rate))

data <- read_csv(here("01_Data", "AJV2_6Nov2019_JLH.csv"))
names(data)

lifetable <- read_csv(here("01_Data", "LifeTable_AJV2_3Dec2022.csv"))
names(lifetable)

```

```{r set figure themes, include = FALSE, echo = FALSE}

singlefigtheme <-theme_classic()+theme(axis.title.x = element_text(size = 18),
                                      axis.title.y = element_text(size = 18),
                                      axis.text.x = element_text(size = 14),
                                      axis.text.y = element_text(size = 14))



singlefigtheme2 <-theme_classic()+theme(axis.title.x = element_text(size = 16),
                                       axis.title.y = element_text(size = 16),
                                       axis.text.x = element_text(size = 12),
                                       axis.text.y = element_text(size = 12))
                                       
                                       
position_jitterdodge(
  jitter.width = NULL,
  jitter.height = 0,
  dodge.width = 0.65,
  seed = NA
)
```

```{r data processing part 1, include = FALSE, echo = FALSE}

#merge data together
all.data.joined <- data %>% 
  left_join(lifetable, by = c("Genotype", 
                              "Spore_level", 
                              "Animal",  
                              "Sex"))

#merge data together
all.data.joined2 <- all.data.joined %>% 
  left_join(df, by = c("Genotype", 
                              "Spore_level", 
                              "Animal"))

```

```{r data processing part 2, include = FALSE, echo = FALSE}
#### Data for plotting ####

inf1 <- all.data.joined2  %>% 
  group_by(Genotype, Spore_level, Animal) %>%
  # count only one tech replicate otherwise, the sample size is inflated! 
  dplyr::filter(Technical_Replicate == "1") %>% 
  dplyr::filter( !Infected_Uninfected %in% "DayZero") %>% # remove animals that die on set up due to user error
  dplyr::filter( !Infected_Uninfected %in% "NA") %>%
  #dplyr::filter( !Infected_Uninfected %in% "Exposed") %>%
  dplyr::filter(mean_feeding_rate > 0.00) %>% # remove negative feeding rates, which represent technical errors
  mutate(meangrowth = mean(Total_Growth, na.rm = T),
         segrowth = sd(Total_Growth, na.rm = T)/sqrt(n()),
         finalsize = mean(Final_Size_mm2, na.rm = T),
         sesize = sd(Final_Size_mm2, na.rm = T)/sqrt(n()),
         meandayfirstclutch = mean(Age_1st_clutch, na.rm = T),
         sefirstclutch = sd(Age_1st_clutch, na.rm = TRUE)/sqrt(n()),
         meanfitnes = mean(Total_Offspring, na.rm = T),
         sefitness = sd(Total_Offspring, na.rm = TRUE)/sqrt(n()),
         meandaydeath = mean(TimeTillDeathDays, na.rm = T),
         sedeathday = sd(TimeTillDeathDays, na.rm = TRUE)/sqrt(n()),
         censored = mean(Censured, na.rm = T),
         meanfeedrate = mean(mean_feeding_rate, na.rm = T),
         sefeedrate = sd(mean_feeding_rate, na.rm = TRUE)/sqrt(n()),
         totInf  = sum(Infected, na.rm = T),
         totSusc = sum(Susceptible, na.rm = T),
         totExp = sum(Exposed, na.rm = T),
         N = sum(totSusc + totInf + totExp),
         probinf =  totInf/(totInf + totSusc + totExp)) %>% 
  mutate(meaninf = sum(1*probinf)) %>% 
  mutate(variance = sum((1^2)*meaninf) - (meaninf^2)) %>% 
  mutate(stdevDinf = sqrt(variance),
         meanspores = mean(Spores_ul,  na.rm = T), 
         sespores = sd(Spores_ul, na.rm = TRUE)/sqrt(n())) %>%
  dplyr::select(Genotype, Spore_level, Infected_Uninfected, 
                Animal, probinf,
                meangrowth, segrowth,
                totInf, totSusc,
                finalsize, sesize,
                meandayfirstclutch,
                sefirstclutch,
                meanfitnes, sefitness,
                meaninf, stdevDinf,  
                meanspores, sespores,
                meandaydeath, sedeathday, censored,
                meanfeedrate, sefeedrate) %>%
  distinct() %>% as.data.frame()

saveRDS(inf1, "inf1.RDS")
```

```{r data processing part 3, include = FALSE, echo = FALSE}
prev <- all.data.joined2  %>% 
  group_by(Genotype, Spore_level) %>%
  # count only one tech replicate otherwise, the sample size is inflated! 
  dplyr::filter(Technical_Replicate == "1") %>% 
  dplyr::filter( !Infected_Uninfected %in% "DayZero") %>% # remove animals that die on set up due to user error
  dplyr::filter( !Infected_Uninfected %in% "NA") %>%
  #dplyr::filter( !Infected_Uninfected %in% "Exposed") %>%
  dplyr::filter(mean_feeding_rate > 0.00) %>%
   mutate(totInf  = sum(Infected, na.rm = T),
         totSusc = sum(Susceptible, na.rm = T),
         totExp = sum(Exposed, na.rm = T),
         N = sum(totSusc + totInf),
         probinf =  totInf/(totInf + totSusc + totExp)) %>% 
  mutate(meaninf = sum(1*probinf)) %>% 
  mutate(variance = sum((1^2)*meaninf) - (meaninf^2)) %>% 
  mutate(stdevDinf = sqrt(variance)) %>%
  dplyr::select(Genotype, Spore_level, probinf,
                meaninf, stdevDinf) %>%
  distinct() %>% as.data.frame()

inf2 <- all.data.joined2  %>% 
  group_by(Genotype, Spore_level) %>%
  # count only one tech replicate otherwise, the sample size is inflated! 
  dplyr::filter(Technical_Replicate == "1") %>% 
  dplyr::filter( !Infected_Uninfected %in% "DayZero") %>% # remove animals that die on set up due to user error
  dplyr::filter( !Infected_Uninfected %in% "NA") %>%
  dplyr::filter( !Infected_Uninfected %in% "Exposed") %>%
  dplyr::filter(mean_feeding_rate > 0.00) %>%
   mutate(meangrowth = mean(Total_Growth, na.rm = T),
         segrowth = sd(Total_Growth, na.rm = T)/sqrt(n()),
         finalsize = mean(Final_Size_mm2, na.rm = T),
         sesize = sd(Final_Size_mm2, na.rm = T)/sqrt(n()),
         meandayfirstclutch = mean(Age_1st_clutch, na.rm = T),
         sefirstclutch = sd(Age_1st_clutch, na.rm = TRUE)/sqrt(n()),
         meanfitnes = mean(Total_Offspring, na.rm = T),
         sefitness = sd(Total_Offspring, na.rm = TRUE)/sqrt(n()),
         meandaydeath = mean(TimeTillDeathDays, na.rm = T),
         sedeathday = sd(TimeTillDeathDays, na.rm = TRUE)/sqrt(n()),
         meanfeedrate = mean(mean_feeding_rate, na.rm = T),
         sefeedrate = sd(mean_feeding_rate, na.rm = TRUE)/sqrt(n())) %>% 
  mutate(meanspores = mean(Spores_ul,  na.rm = T), 
         sespores = sd(Spores_ul, na.rm = TRUE)/sqrt(n())) %>%
  dplyr::select(Genotype, Spore_level, 
                meangrowth, segrowth,
                finalsize, sesize,
                meandayfirstclutch,
                sefirstclutch,
                meanfitnes, sefitness,
                meanspores, sespores,
                meandaydeath, sedeathday,
                meanfeedrate, sefeedrate) %>%
  distinct() %>% as.data.frame()

left_join(prev, inf2, by=c('Genotype','Spore_level'))->inf3

saveRDS(inf3, "inf3.RDS")

```

#### Plot mean Feeding with mean spores

set the y-axis for each genotype separately: M281 eats much more than
everyone else adjusting scale so differences among spore levels for
other genotypes are easily seen.

#### Multi-panel with susceptibility

```{r plotting prevalence,  echo = FALSE}
set.seed(566)
ggplot(transform(inf1,
      Genotype=factor(Genotype,levels=c("Standard","Midland 281","Midland 252", "A45"))), aes(x = Spore_level, color = as.factor(Spore_level), y = probinf*100)) +
  geom_rect(xmin = -Inf, xmax = 25, ymin = -Inf, ymax = 300, fill = "lightgrey", color = "NA") +
  geom_jitter(size = 5, width =10, height = 0.00002, alpha = 0.2)+
  singlefigtheme+
  labs(y = expression("Susceptibility (% infected)"), x = expression("Pathogen dose (no. mL"^-1*")")) + 
  facet_wrap(~ Genotype, nrow = 4) +
  scale_color_manual(values = c("darkcyan", "goldenrod1", "darkmagenta")) +
  stat_summary(fun = "mean",
                geom = "point",
               color = rep(c("darkcyan", "goldenrod1", "darkmagenta"),4),
               size = 10) +
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 0.75),  
        legend.position = "none",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        strip.text.x = element_text(size = 12))+
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100))+
  scale_x_continuous(limits = c(-10, 370), breaks = c(0, 150, 300)) ->Fig2
```

# Plot: Hosts differ in their immune-mediated changes in feeding behavior
## Showing results in this layout to emphasize the difference among the genotypes

*Note, this requires adjusting the y-axis since one genotype consumes
much more relative to the others. Grey shading emphasizes the comparison
to pathogen-free environments. The focus here is on animals that were
either unexposed or infected, thus we will exclude animals that were
exposed but where infections were either cleared or too low to detect.

```{r plotting feeding rates,  echo = FALSE}

inf1 %>% 
  filter(Infected_Uninfected != "Exposed") %>%
  transform(Genotype=factor(Genotype,levels=c("Standard","Midland 281","Midland 252", "A45"))) %>%
  ggplot(aes(x = Spore_level, 
                      fill = as.factor(Spore_level), 
                      color = as.factor(Spore_level), 
                      y = meanfeedrate)) +
  geom_rect(xmin = -Inf, xmax = 15.5, 
            ymin = -Inf, ymax = Inf, 
            fill = "lightgrey", color = "NA", alpha = 0.01) +
  geom_point(aes(size = 5), pch =1) +
  scale_shape_manual(values = 1)+  
  facet_wrap(~ Genotype, scales = "free_y", nrow =4) +
  stat_summary(fun.data = mean_se, size = 1.5, alpha = 1) +
  scale_fill_manual(values = c("darkcyan", "goldenrod1", "darkmagenta"))+
  scale_color_manual(values = c("darkcyan", "goldenrod1", "darkmagenta")) +
  labs(y = expression("LN Feeding rate (mL"^-1* ind^-1* hr^-1*")"), x = expression("Pathogen dose (no. mL"^-1*")"))+
  singlefigtheme+
   theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size = 0.75),  
        legend.position = "none",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        strip.text.x = element_text(size = 12))+
  #scale_y_continuous(limits = c(0.05, 0.55), breaks = c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5))+
  scale_x_continuous(limits = c(0, 300), breaks = c(0, 150, 300)) -> Fig3

grouped_fig<- Fig2 + Fig3

ggsave("Figure2.png", grouped_fig, height = 12, width = 8, dpi = 600)
```

Most susceptible genotype showed strongest illness mediated anorexia
relative to less susceptible genotypes.

```{r plotting feeding rates with host growth rates, echo = FALSE}
plotgrowth <- inf3 %>% 
  filter(Spore_level != 0) %>%
  ggplot(aes(y = meangrowth, 
             x = meanfeedrate, 
             ymin = meangrowth - segrowth,
             ymax = meangrowth + segrowth, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  stat_poly_line(aes(y = meangrowth, 
             x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0) +
  stat_poly_eq(aes(y = meangrowth, 
             x = meanfeedrate, group =1), method="lm") +
  geom_point(position = position_dodge(0.2), size = 5)+
  geom_errorbar(aes(ymin = meangrowth - segrowth,
                    ymax = meangrowth + segrowth,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 5) +
  scale_shape_manual(values=c(16,15))+
  #scale_color_manual(values=c("#F8766D", "#7CAE00", "#C77CFF"))+
  ylab("Total growth (final - intial size, mm)") + 
  labs(x = expression("LN Feeding rate (mL"^-1* ind^-1* hr^-1*")")) +
  singlefigtheme2+
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "none")+
  scale_x_continuous(limits = c(0.05, 0.36), breaks = c(0.10, 0.2, 0.3))

plotgrowth

```

# Some genotypes exhibit higher total reproduction or fecundity overcompoensation, but only at certain spore levels

```{r plotting feeding rates with host fitness (fecundity),  echo = FALSE}
plotfitness <- inf3 %>% 
  filter(Spore_level != 0) %>%
  ggplot(aes(y = meanfitnes, 
             x = meanfeedrate, 
             ymin = meanfitnes - sefitness,
             ymax = meanfitnes + sefitness, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  stat_poly_line(aes(y = meanfitnes, 
             x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0) +
  stat_poly_eq(aes(y = meanfitnes, 
             x = meanfeedrate, group =1), method="lm") +
   #geom_smooth(aes(y = meanfitnes, 
   #          x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0)+
  geom_point(position = position_dodge(0.2), size = 5)+
  geom_errorbar(aes(ymin = meanfitnes - sefitness,
                    ymax = meanfitnes + sefitness,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 5) +
  scale_shape_manual(values=c(16,15))+
  #scale_color_manual(values=c("#F8766D", "#7CAE00", "#C77CFF"))+
  labs(y = expression("Total reproduction (# host" ^-1*")")) + 
  labs(x = expression("LN Feeding rate (mL"^-1* ind^-1* hr^-1*")")) +
  singlefigtheme2+
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))+
  theme(legend.position = "none")+ 
  scale_y_continuous(limits = c(1.0, 8.0), breaks = c(1.50, 3.50, 5.50, 7.50))+
  scale_x_continuous(limits = c(0.05, 0.36), breaks = c(0.10, 0.2, 0.3))
plotfitness


summary(lm(meanfitnes ~ meanfeedrate, family = gaussian(link = "identity"), data= filter(inf3, Spore_level != 0)))
```

```{r plotting feeding rates with spore yield/within-host spore density,  echo = FALSE}

plotsporeyield <- inf3 %>% 
  filter(Spore_level != 0) %>%
  ggplot(aes(y = meanspores, 
             x = meanfeedrate, 
             ymin = meanspores - sespores,
             ymax = meanspores + sespores, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  stat_poly_line(aes(y = meanspores, 
             x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0) +
  stat_poly_eq(aes(y = meanspores, 
             x = meanfeedrate, group =1), method="lm") +
  geom_point(position = position_dodge(0.2), size = 5)+
  geom_errorbar(aes(ymin = meanspores - sespores,
                    ymax = meanspores + sespores,
                    width = 0)) +
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 5) +
  scale_shape_manual(values=c(16,15))+
  #scale_color_manual(values=c("#F8766D", "#7CAE00", "#C77CFF"))+
  labs(y = expression("Spore yield (spores host"^-1* "x 10"^3* ")")) + 
  xlab("")+
  singlefigtheme2+
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75))+  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
  theme(legend.position = c(0.70, 0.80), 
        legend.box = "horizontal",
        legend.key.size = unit(0.01, 'cm'))+
  labs(shape = "Pathogen dose", color = "Host genotype")+
  scale_y_continuous(limits = c(0, 125), breaks = c(0, 25, 50, 75, 100))+
  scale_x_continuous(limits = c(0.05, 0.36), breaks = c(0.10, 0.2, 0.3))
plotsporeyield


summary(lm(meanspores ~ meanfeedrate, family = gaussian(link = "identity"), data= filter(inf3, Spore_level != 0)))
```

# hosts ate significantly less when exposed to more pathogen spores.

```{r plotting feeding rates and infection frequency,  echo = FALSE}
plotinfection <- inf3 %>% 
  filter(Spore_level != 0) %>%
  ggplot(aes(y = probinf*100, 
             x = meanfeedrate, 
             shape = as.factor(Spore_level),
             color = as.factor(Genotype)))+
  stat_poly_line(aes(y = probinf*100, 
             x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0) +
  stat_poly_eq(aes(y = probinf*100, 
             x = meanfeedrate, group =1), method="lm") +
  #geom_smooth(aes(y = probinf*100, x = meanfeedrate, group =1), method="lm", color = "black", alpha = 0)+
  geom_point(position = position_dodge(0.2), size = 5, alpha = 0.7)+
  geom_errorbarh(aes(xmin = meanfeedrate - sefeedrate, 
                     xmax = meanfeedrate + sefeedrate,
                     height = 0)) +
  geom_point(position = position_dodge(0.2), size = 5, alpha = 0.7) +
  scale_shape_manual(values=c(16,15))+
  #scale_color_manual(values=c("#F8766D", "#7CAE00", "#C77CFF"))+
  ylab("Susceptibility (% infected)")  + 
  xlab("")+
  singlefigtheme2+
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", 
                                    fill = NA, size = 0.75),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        legend.position = "none")+
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100))+
  scale_x_continuous(limits = c(0.05, 0.36), breaks = c(0.10, 0.2, 0.3))
plotinfection 

summary(lm(probinf*100 ~ meanfeedrate, family = gaussian(link = "identity"), data= filter(inf3, Spore_level != 0)))
```

#Feeding and Susceptibility, Spore Yield, Fitness, and Growth

```{r combining figures part 1, include = FALSE, echo = FALSE}
Figure4 <- (plotinfection + plotsporeyield)/ (plotfitness + plotgrowth) 
Figure4 

ggsave("Fig4.png", Figure4, height = 10, width = 10.5, dpi = 600)
```


# STATS SECTION
```{r stats section part 1, include = FALSE, echo = FALSE}
total <- all.data.joined2  %>%
  dplyr::filter(Technical_Replicate == "1") %>% 
  dplyr::filter(!Infected_Uninfected %in% "DayZero") %>% # remove animals that die on set up due to user error
  dplyr::filter(!Infected_Uninfected %in% "NA") %>%
  dplyr::filter(!Sex %in% "M") %>% 
  dplyr::filter(mean_feeding_rate > 0.00) ### remove negative feeding rates b/c they represent technical error
  #dplyr::filter(!Infected_Uninfected %in% "Exposed") 

saveRDS(total, 'total.RDS')
```

## Table 1
```{r stats for table 1 susceptibility, echo = FALSE}

#### Table 1: ####
infected <- total %>% 
  filter(Spore_level > 0, na.rm = TRUE) %>%
  filter(Genotype != "Midland 281")

y <- with(infected, cbind(Infected, (Susceptible + Infected + Exposed)))


modinf1 <- glm(y ~ Genotype*as.factor(Spore_level),
             family = binomial,
             data = infected) 

modinf2 <- glm(y ~ Genotype
              + as.factor(Spore_level),
              family = binomial,
              data = infected) 

modinf3 <- glm(y ~ Genotype
              + as.factor(Spore_level)
              + mean_feeding_rate,
              family = binomial,
              data = infected) 

bbmle::AICctab(modinf1, modinf2, modinf3)

#### Table 1 ## ####
#plot(modinf2)
summary(modinf2)
stats1 <- car::Anova(modinf2, type = 'III')
stats1
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

## Table 2
```{r stats Table 2 feeding rates,  echo = FALSE}
#### Model: Does mean feeding rate differ across spore levels, genotype, and infection status? ####
#### Full model - singular so doesn't converge.
# mod1a <- glm(mean_feeding_rate ~ Genotype*Size_mm2*Infected_Uninfected*Spore_level, 
#              family = gaussian(link = "log"),
#              data = total) 
# 
# summary(mod1a)
# car::Anova(mod1a, type = 'III')

#### Next attempt at full model - interaction terms render the model singular, so do not include
mod1b <- glm(mean_feeding_rate ~ Genotype*Size_mm2 + Spore_level,
            family = gaussian(link = "log"),
            data = filter(total, Infected_Uninfected != "Exposed")) 

summary(mod1b)
car::Anova(mod1b, type = 'III')
car::Anova(mod1b, test = "LR")


mod1c <- glm(mean_feeding_rate ~ Genotype + Size_mm2  + Spore_level,
             family = gaussian(link = "log"),
             data = filter(total, Infected_Uninfected != "Exposed")) 


mod1d <- glm(mean_feeding_rate ~ Genotype*Spore_level + Size_mm2,
            family = gaussian(link = "log"),
            data = filter(total, Infected_Uninfected != "Exposed")) 

summary(mod1d)
car::Anova(mod1d, type = 'III')
car::Anova(mod1d, test = "LR")
bbmle::AICctab(mod1b, mod1c, mod1d)


#plot(mod1c) 
#### Table 2 ####
summary(mod1c)
stats1 <- car::Anova(mod1c, type = 'III')

Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))


#### post hoc analysis ####
marginal = emmeans(mod1c, ~ Genotype)
pairs(marginal)

```

## Table 3a
```{r stats host fitness,  echo = FALSE}
#### Host GROWTH ####

#remove exposed but uninfected individuals and remove Midland 281 because there is only infected individual per exposure level
use<- inf1 %>%
  filter(Genotype != "Midland 281")%>%
  filter(Infected_Uninfected != "Exposed")

#### Estimate Population Distributions ####
# Population dist of Pop A
library(fitdistrplus)

fitdistrplus::descdist(as.numeric(na.omit(use$meanfitnes),
                                  use.names = F),
                       boot = 1000, discrete = T)

with(use, hist(meanfitnes))


pois.fit <- glm(formula = meanfitnes ~ meangrowth
                + Genotype
                + Spore_level,
                family = poisson(link = "log"),
                data = use)

nb.fit <- glm.nb(formula = meanfitnes ~ meangrowth
                 + Genotype
                 + Spore_level,
                 data = use)

nb.fit1 <- glm.nb(formula = meanfitnes ~ meangrowth
                 + Genotype
                 + Spore_level
                 + Spore_level*Genotype,
                 data = use)

ZIP.fit <- zeroinfl(formula = meanfitnes ~  meangrowth 
                    + Genotype 
                    + Spore_level,
                    data = use,
                    dist = "poisson", # default log link
                    link = "logit") # for zero infl link

ZINB.fit <- zeroinfl(formula = meanfitnes ~ meangrowth 
                     + Genotype 
                     + Spore_level,
                     data = use,
                     dist = "negbin", # default log link
                     link = "logit") # for zero infl link


bbmle::AICctab(pois.fit, nb.fit, nb.fit1)



#plot(nb.fit1)
stats1 <- car::Anova(nb.fit1, type = 'III')
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

## Table 3b
```{r stats host growth rates,  echo = FALSE}
#### HOST GROWTH ####

#### Estimate Population Distributions ####
# Population dist of Pop A
fitdistrplus::descdist(as.numeric(na.omit(use$meangrowth),
                                  use.names = F),
                       boot = 1000, discrete = T)



modgrowth1 <- glm(meangrowth ~ Spore_level + Genotype,
                  family = gaussian(link = "identity"),
                  data = use)

car::Anova(modgrowth1, type = 'III')


modgrowth2 <- glm(meangrowth ~ Spore_level*Genotype,
                  family = gaussian(link = "identity"),
                  data = use)

car::Anova(modgrowth2, type = 'III')

bbmle::AICctab(modgrowth1, modgrowth2)


plot(modgrowth1)
stats1 <- car::Anova(modgrowth1, type = 'III')
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)

autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))


#### post hoc analysis host growth ####
marginal = emmeans(modgrowth1, ~ Genotype)
pairs(marginal)

```

## Table 3c
```{r stats_host_survival, echo = FALSE}
#### Estimate Population Distributions ####
# Population dist of Pop A
fitdistrplus::descdist(as.numeric(na.omit(use$meandaydeath),
                                  use.names = F),
                       boot = 1000, discrete = T)

with(use, hist(meandaydeath))


modsurv1 <- glm(meandaydeath ~ Spore_level + Genotype,
                  family = gaussian(link = "identity"),
                  data = use)

car::Anova(modsurv1, type = 'III')


modsurv2 <- glm(meandaydeath ~  Spore_level*Genotype,
                  family = gaussian(link = "identity"),
                  data = use)

car::Anova(modsurv2, type = 'III')

bbmle::AICctab(modsurv1, modsurv2)


#plot(modsurv1)
stats1 <- car::Anova(modsurv1, type = 'III')
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))


#### post hoc analysis host growth ####
marginal = emmeans(modsurv1, ~ probinf|Genotype)
pairs(marginal)
```

## Table 4a_1 Susceptibility
```{r stats patterns across all genotypes,  echo = FALSE}
#### Model: Across all genotypes does the probability of infection differ across feeding rates, final body size (surface area), spore levels  ? ####

y <- with(infected, cbind(Infected, (Susceptible + Infected + Exposed)))


#### Across all genotypes ####
mod2m <- glm(y ~ mean_feeding_rate*Size_mm2
             + as.factor(Spore_level),
             family = binomial,
             data = infected) 

mod3m <- glm(y ~ mean_feeding_rate + Size_mm2,
             family = binomial,
             data = infected) 



bbmle::AICctab(mod3m, mod2m)

#### Table 4a ## ####
#plot(mod3m)

summary(mod3m)
stats1 <- car::Anova(mod3m, type = 'III')
stats1
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

## Table 4b_1 Susceptibility w/ genetic variation
```{r stats, feeding rates and infection frequency - when accounting for genotypic differences,  echo = FALSE}

mod2h <- glm(y ~ mean_feeding_rate*Size_mm2
             + as.factor(Genotype)
             + as.factor(Spore_level), 
             family = binomial,
             data = infected) 


car::Anova(mod2h, test = "Wald")


mod2i <- glm(y ~ mean_feeding_rate + Size_mm2
             + as.factor(Genotype)
             + as.factor(Spore_level), 
             family = binomial,
             data = infected) 

car::Anova(mod2i, test = "Wald")



bbmle::AICctab(mod2h, mod2i)

car::Anova(mod2i, type = 'III')

#Table 4b
stats1 <- car::Anova(mod2i, type = 'III')
stats1
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

## Table 4a_2 Spore yield
```{r stats Table 4a spore yield,  echo = FALSE}
total <- total %>%
  mutate(Spore_level_fct = factor(Spore_level))

# Examine spore yield in animals that were actually infected

totalpos <- total %>% 
  filter(Genotype != 'Midland 281')%>%
  filter(Spores_ul>0)

#### Spore yield and Anorexia
#### Patterns across all genotypes ####

modfeedspores1 <- glm(Spores_ul ~ mean_feeding_rate*Size_mm2 
                     + Spore_level_fct,
                     family = gaussian(link = "identity"),
                     data = totalpos)

car::Anova(modfeedspores1, type = 'III')


modfeedspores2 <- glm(Spores_ul ~ mean_feeding_rate+Size_mm2 
                     + Spore_level_fct*Final_Size_mm2,
                     family = gaussian(link = "identity"),
                     data = totalpos)

car::Anova(modfeedspores2, type = 'III')

modfeedspores3 <- glm(Spores_ul ~ mean_feeding_rate+Size_mm2 
                      + Spore_level_fct+Final_Size_mm2,
                      family = gaussian(link = "identity"),
                      data = totalpos)


modfeedspores4 <- glm(Spores_ul ~ Spore_level_fct+Final_Size_mm2,
                      family = gaussian(link = "identity"),
                      data = totalpos)


car::Anova(modfeedspores4, type = 'III')


AIC(modfeedspores1, modfeedspores2, modfeedspores3, modfeedspores4)



#### Table ####
 summary(modfeedspores4)
 stats1 <- car::Anova(modfeedspores4, type = 'III')
 stats1
 Term <- rownames(stats1)
 stats1 <- cbind(Term, stats1)
 autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

## Table 4b_2 Spore yield w/ genetic variation
```{r stats Table 4b spore yield,  echo = FALSE, warning = FALSE}

# Examine spore yield in animals that were actually infected

modfeedspores <- glm(Spores_ul ~ mean_feeding_rate*Size_mm2 
                  + Spore_level_fct
                  + Genotype
                  + Final_Size_mm2,
                  family = gaussian(link = "identity"),
                  data = totalpos)

car::Anova(modfeedspores, type = 'III')


modfeedsporesb <- glm(Spores_ul ~ mean_feeding_rate + Size_mm2
                     + Spore_level_fct
                     + Genotype
                     + Final_Size_mm2,
                     family = gaussian(link = "identity"),
                     data = totalpos)

car::Anova(modfeedsporesb, type = 'III')


modfeedsporesc <- glm(Spores_ul ~  Size_mm2 
                      + Spore_level_fct
                      + Genotype
                      + Final_Size_mm2,
                      family = gaussian(link = "identity"),
                      data = totalpos)

car::Anova(modfeedsporesc, type = 'III')


modfeedsporesd <- glm(Spores_ul ~ Spore_level_fct
                      + Genotype
                      + Final_Size_mm2,
                      family = gaussian(link = "identity"),
                      data = totalpos)

car::Anova(modfeedsporesd, type = 'III')


modfeedsporese <- glm(Spores_ul ~ Spore_level_fct
                      + Genotype,
                      family = gaussian(link = "identity"),
                      data = totalpos)

car::Anova(modfeedsporese, type = 'III')


AIC(modfeedspores, modfeedsporesb, modfeedsporesc, modfeedsporesd,  modfeedsporese)


#### Table 4b ####
summary(modfeedsporesd)
stats1 <- car::Anova(modfeedsporesd, type = 'III')
stats1
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))


#### post hoc analysis ####
marginal = emmeans(modfeedsporesd, ~ Genotype|Spore_level_fct)
pairs(marginal)
```

## Susceptibility and Spore yield
```{r stats susceptibilty and spore yield,  echo = FALSE, warnings = FALSE}

with(inf1, cor.test(probinf, meanspores*finalsize + Spore_level, method ="pearson"))

library(MASS)
library(pscl)
require(pscl)


total <- all.data.joined2  %>%
  dplyr::filter(Technical_Replicate == "1") %>% 
  dplyr::filter(!Infected_Uninfected %in% "DayZero") %>% # remove animals that die on set up due to user error
  dplyr::filter(!Infected_Uninfected %in% "NA") %>%
  dplyr::filter(!Sex %in% "M") %>% 
  dplyr::filter(mean_feeding_rate > 0.00) ### remove negative feeding rates b/c they represent technical error
#dplyr::filter(!Infected_Uninfected %in% "Exposed") 

total <- total %>%
  mutate(Spore_level_fct = factor(Spore_level))


total2 <- total[!complete.cases(total), ]


#### Estimate Population Distributions ####
# Population dist of Pop A
library(fitdistrplus)
fitdistrplus::descdist(as.numeric(na.omit(total2$Total_Fecundity),
                    use.names = F),
         boot = 1000, discrete = T)

with(total, hist(Total_Fecundity))


pois.fit <- glm(formula = Total_Fecundity ~ Total_Growth
                + Genotype
                + Spore_level_fct 
                + Infected_Uninfected,
                family = poisson(link = "log"),
                data = total)

nb.fit <- glm.nb(formula = Total_Fecundity ~ Total_Growth 
                 + Genotype
                 + Spore_level_fct 
                 + Infected_Uninfected,
                 data = total)

# ZIP.fit <- zeroinfl(formula = Total_Fecundity ~  Total_Growth 
#                     + Genotype 
#                     + Spore_level_fct 
#                     + Infected_Uninfected,
#                     data = total,
#                     dist = "poisson", # default log link
#                     link = "logit") # for zero infl link
# 
# ZINB.fit <- zeroinfl(formula = Total_Fecundity ~ Total_Growth 
#                      + Genotype 
#                      + Spore_level_fct 
#                      + Infected_Uninfected,
#                      data = total,
#                      dist = "negbin", # default log link
#                      link = "logit") # for zero infl link


bbmle::AICctab(pois.fit, nb.fit)


nb.fit1 <- glm.nb(formula = Total_Fecundity ~ Total_Growth
                 + Genotype
                 + Infected_Uninfected,
                 data = total)

bbmle::AICctab(pois.fit, nb.fit, nb.fit1)
anova(nb.fit1, test = "Chisq")



#plot(nb.fit1)
stats1 <- car::Anova(nb.fit1, type = 'III')
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))

```

## Feeding Rate
```{r stats feeding rates and infection frequency across all genotypes,  echo = FALSE}
#### Across all genotypes: Susceptibility and Anorexia/Hyperphagia
modfeedinf <- glm(meanfeedrate ~ probinf+finalsize 
                  + Spore_level,
                  family = gaussian(link = "identity"),
                  data = filter(inf1, Spore_level != 0))

car::Anova(modfeedinf, type = 'III')

#### Across all genotypes: Spore yield and Anorexia/Hyperphagia
modfeedspore <- glm(meanfeedrate ~ meanspores+finalsize 
                  + Spore_level,
                  family = gaussian(link = "identity"),
                  data = filter(inf1, Spore_level != 0))

car::Anova(modfeedspore, type = 'III')
```

## Feeding Rate with genetic variation
```{r stats feeding rates and infection frequency, echo = FALSE}
#### Susceptibility and Anorexia/Hyperphagia
modfeedinf <- glm(meanfeedrate ~ probinf*finalsize 
                  + Spore_level
                  + Genotype,
                  family = gaussian(link = "identity"),
                  data = inf1)

car::Anova(modfeedinf, type = 'III')


modfeedinfb <- glm(meanfeedrate ~ probinf*finalsize 
                   + Genotype,
                   family = gaussian(link = "identity"),
                   data = inf1)

car::Anova(modfeedinfb, type = 'III')



modfeedinfc <- glm(meanfeedrate ~ probinf*finalsize 
                   + Spore_level
                   + Genotype,
                   family = gaussian(link = "identity"),
                   data = inf1)

car::Anova(modfeedinfc, type = 'III')


modfeedinfd <- glm(meanfeedrate ~ probinf*finalsize 
                   + Genotype,
                   family = gaussian(link = "log"),
                   data = inf1)

car::Anova(modfeedinfd, type = 'III')



bbmle::AICctab(modfeedinf, modfeedinfb, modfeedinfc, modfeedinfd)


#plot(modfeedinfb)
summary(modfeedinfd)
stats1 <- car::Anova(modfeedinfd, type = 'III')
stats1
Term <- rownames(stats1)
stats1 <- cbind(Term, stats1)
autofit(colformat_num(x = flextable(stats1), j = "Pr(>Chisq)", digits = 4))
```

# Additional Figure
## Multi-panel with spore yield
```{r plotting spore yield, echo = FALSE}
inf1 %>% 
  filter(Infected_Uninfected != "Exposed") %>%
  transform(Genotype=factor(Genotype,levels=c("Standard","Midland 281","Midland 252", "A45"))) %>%
  ggplot(aes(x = Spore_level, color = as.factor(Spore_level), y = meanspores)) +
  geom_rect(xmin = -Inf, xmax = 15.5, ymin = -Inf,ymax = Inf, fill = "lightgrey", color = "NA", alpha = 0.01) +
    geom_point(position = position_dodge(0.2), size = 5, alpha = 0.30) +
  facet_wrap(~ Genotype, nrow =2) +
  stat_summary(fun.data = mean_se, size = 1.5, alpha = 1.75, position = position_dodge(0.2)) +
  scale_color_manual(values = c("darkcyan", "goldenrod1", "darkmagenta")) +
  singlefigtheme+ 
  labs(x= expression("Spore dose (no. mL"^-1*")"), y = expression("Susceptibility (spore yield)"))+
  theme(panel.spacing = unit(1.05, "lines"),
        panel.border = element_rect(color = "black", fill = NA, size =1),  
        legend.position = "none",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        strip.text.x = element_text(size = 12))+
  scale_y_continuous(limits = c(0, 125), breaks = c(0, 25, 50, 75, 100, 125))+
  scale_x_continuous(limits = c(0, 300), breaks = c(0, 150, 300))

```